\section{Discussion}
\label{sec:discussion}

This year's participation represents the most significant architectural evolution of our BioASQ pipeline since we began competing. Below we discuss the key findings, grounding each conclusion in the official results presented in Section~\ref{sec:results} and the internal validation experiments.

\subsection{Retrieval}

The migration from PyTerrier PISA to pg\_textsearch for BM25 and from flat-file storage to Qdrant for dense retrieval proved successful not primarily in raw speed, but in operational reliability. Across all four batches, BM25 served as the backbone of every submission, and no index-corruption or synchronization issues were encountered---a marked improvement over previous editions where index maintenance consumed significant engineering time. The PostgreSQL-centric architecture, where documents, BM25 indexes, and metadata coexist in a single database, reduced the risk of configuration errors and simplified the submission pipeline.

Our internal validation results (Table~\ref{tab:internal-retrieval}) demonstrated that hybrid retrieval substantially outperforms BM25 alone: RRF fusion improved MRR from 0.549 to 0.696 (+27\%) and R@100 from 0.373 to 0.406 (+9\%). However, this pattern was not mirrored in the official results, where systems using hybrid retrieval placed in worse ranks across multiple batches, when compared to BM25-only retrieval ones. The same applies to RRF, where it consistently outperformed weighted sum on MAP in internal evaluations, but failed to produce a clear ranking advantage in the official results. This discrepancy highlights the challenges of overfitting to internal validation sets and underscores the importance of cross-batch consistency as a more robust signal of retrieval quality than peak single-batch performance.

The reranker ensemble proved essential. Our best reranker configuration (BGE-reranker-v2-m3 applied to weighted-sum fusion) achieved an MRR of 0.738 in internal validation, substantially above the un-reranked baselines. The LLaMA Nemotron reranker achieved near-perfect validation scores (MAP-bioasq@10 of 0.9995), though we note that validation scores on 13B data do not guarantee equivalent gains on new test sets. We incorporated dense retrieval results into the negative sampling process for reranker training, which we hypothesize helps the reranker generalize across both BM25 and dense retrieval paradigms; however, this specific claim awaits formal ablation testing. While the official ranking results validate these cautions, a new finding arises: using the best reranker configurations was not the best option. In Batch~1 and Batch~2, systems using the best reranker configurations got outperformed by the ones that use all of them. Nonetheless, internal validation of sampling strategies for training the reranker showed that curriculum-based hard negative mining is particularly beneficial when model capacity is limited and the training signal from random negatives is insufficient to learn fine-grained relevance distinctions. These results validate the choice of the ShifterSampler as the default for our production reranker training pipeline.

Context-1 demonstrated the highest R@100 (0.453) in internal testing, suggesting strong potential as a recall-oriented first-stage method. However, its lower MRR (0.508) compared to hybrid+reranker configurations indicates that it is best used as a document source for downstream re-ranking rather than as a standalone retrieval solution. Its bad performance on official results (placed in the top 50 in MAP ranks) demonstrate that although an interesting approach, it is not yet competitive with more established retrieval methods. The discrepancy between internal validation and official results for Context-1 may be due to differences in question distributions, batch conditions, or the specific implementation of Context-1 in the competition pipeline.

Most changes to the retrieval pipeline appear to have performed worse, bringing no improvement to the official results. However, human evaluation is still ongoing, which may reveal more nuanced differences between configurations that are not fully captured by the official automated metrics. As such, we are waiting for the human evaluation results before drawing final conclusions about the impact of specific retrieval changes, particularly regarding the use of Context-1 and the effectiveness of different fusion strategies.

\subsection{Generation}

The LLM-as-a-judge judge's reliance on generating full candidate answers from every model before evaluation improved our pipeline, as proved in Batch~1 and Batch~2, with a focus on the latter. It outperformed ensemble and majority voting, as well as the agent quorum approach on some submissions. However, human-based evaluation is still on hold, which might change the conclusions on this approach. Nonetheless, the judge remains a promising tool for exact answer types with objectively verifiable correctness.

The agent quorum mechanism produced our strongest Phase~A+ and Phase~B results for both exact and ideal answers. In Batch~3, the quorum-based configurations achieved a perfect yes/no accuracy (rank 1) and factoid strict accuracy rank 1 (\texttt{bioinfo-0} and \texttt{bioinfo-3}). In Phase~B Batch~4, \texttt{bioinfo-3} achieved rank 4 in both factoid strict and lenient accuracy---our best factoid performance across all phases and batches. Also, across the entire Phase~B submissions, the quorum submissions consistently outperformed the other ones, which validates the core hypothesis that structured multi-agent debate can enhance answer quality by leveraging diverse reasoning paths and cross-validation among models. The adaptive document retention strategy, where agents iteratively refine their context based on debate outcomes, appears to be a key innovation that balances the depth of reasoning with computational efficiency.

A clear finding from our model-scale experiments was that smaller models (Gemma~4~E2B and E4B, Nemotron-3-Nano-4B) performed competitively with, and in several batches outperformed, larger models on most metrics, especially the precision-oriented ones, such as F1 score. We attribute this to the tendency of smaller models to produce more focused representations, reducing over-elaboration and overfitting to spurious patterns in the retrieved context. The exception was list-type questions, where larger models' broader context retention proved advantageous for tracking multiple entities across documents.

A practical consideration is the computational cost of the agent quorum. Running multiple debate rounds with several large LLMs is expensive in terms of both inference cost and wall-clock time. For our largest configurations (e.g., Agents v2 with Nemotron-120B, Grok-4.1, Gemini-3-Flash, Gemini-2.5-Flash, and GPT-5-Mini, each producing multi-turn reasoning), a single question could consume substantial API credits. In many scenarios, this cost is difficult to justify relative to simpler ensembling or single-model approaches. However, the finding that lightweight local models (Gemma~4~E2B/E4B, Nemotron-3-Nano-4B) perform competitively fundamentally changes this calculus: these models can run on consumer-grade GPUs with negligible inference cost, making iterative agent loops and multi-turn debate economically viable. For tasks requiring sustained agentic reasoning—particularly where the cost of an incorrect answer is high—lightweight quorum configurations represent a practical and cost-effective solution.

The LLM-as-a-judge framework was deployed in two specific contexts: Phase~B Batch~1 (two submissions with top-$k$ answer selection at $k=3$ and $k=5$) and Phase~A+ Batch~2 (top-$k=1$ and $k=3$). The judge pipeline operates by first generating candidate answers from multiple model-prompt-context combinations (4 models $\times$ up to 6 prompts $\times$ 2 context sources), then using an LLM (Gemini~2.5~Flash) to score each answer on correctness, faithfulness, and completeness, selecting the best candidates and finally merging them with a separate model (Claude~Sonnet~4.6). While conceptually sound, the judge was used less extensively than the quorum for several reasons. The quorum's structured debate produced interpretable reasoning trails that aided debugging, and its adaptive document retention avoided the cost of generating full candidate answers from every model before evaluation. The judge remains valuable for exact answer types with objectively verifiable correctness, and a hybrid judge+quorum approach is a promising direction.

Just like with retrieval, human-based evaluation results have not yet been completed, and the final results may change the conclusions that are not fully captured by automated metrics.

\subsection{Future Work}

Several directions emerge from this year's findings. Most of the changes developed in this edition have worsened the overall performance of the systems on Phase A. For example, although the strong internal validation results for Context-1's recall could motivate integrating Context-1 as a first-stage retrieval method in competition submissions, the official results contradict this finding; official, human-based evaluation results, as well as further experimentation, are needed to evaluate its performance across more diverse question types and batch conditions. SPLADE and ColBERT remain promising retrieval approaches for future editions. For generation, dynamic prompt selection based on question type---particularly specialized handling of list questions---and the integration of the LLM judge as a post-quorum quality filter are immediate priorities. Improving snippet extraction quality should yield downstream benefits for both retrieval evaluation and agent quorum answer precision.

A key finding that warrants deeper investigation is the competitive performance of smaller language models relative to their larger counterparts in the agent quorum. Across multiple batches, the lightweight configurations (Gemma~4~E2B, E4B, and Nemotron-3-Nano-4B) performed comparably to much larger models on most metrics, with lower inference cost and latency. These results validate the use of lightweight models for the quorum and suggest that further testing with expanded evaluation protocols (covering more batches, question types, and model combinations) could refine our understanding of when and where small models suffice, potentially leading to more cost-effective submission strategies. The worse performance of those small models in list-type questions highlights the need for more nuanced approaches to model selection and deployment. The agent quorum itself would also benefit from more extensive testing and evaluation, particularly regarding the impact of debate round count, agent pool diversity, and convergence criteria on answer quality. Besides that, more benchmark testing against other explored approaches is needed to fully understand their relative strengths and weaknesses.
