\section{Introduction}
\label{sec:introduction}

Biomedical question answering remains a critical and challenging task in natural language processing, driven by the accelerating growth of biomedical literature. Systems capable of retrieving relevant documents and generating accurate, evidence-based answers to complex biomedical questions are essential for researchers and clinicians navigating an ever-expanding knowledge base. The BioASQ Task~B challenge~\cite{BioASQ2026,QAcorpusBioASQ} has consistently provided a rigorous benchmark for evaluating and advancing these technologies, requiring participants to retrieve relevant PubMed documents (Phase~A) and generate answers from them (Phases~A+~and~B).

Our team, BIT.UA from the University of Aveiro, has participated in several consecutive editions of the BioASQ challenge~\cite{almeida2024bit, jonker2025bit}. Each year, we have iteratively refined our pipeline based on lessons learned from both automatic metrics and, more critically, human evaluation results. The 13th edition~\cite{jonker2025bit} revealed a persistent misalignment between automatic evaluation metrics and human-judged answer quality, motivating a fundamental rethinking of our approach. In that edition, we also observed that Dense Pseudo Relevance Feedback (DPRF) yielded consistent improvements in retrieval, while our generation systems remained our weakest component.

For the 14th edition, we undertook a major architectural overhaul, with new reranker models. The entire codebase was restructured with a focus on modularity, enabling cleaner separation of concerns and more flexible experimentation. In Phase~A, we replaced the PyTerrier PISA indexing system with PostgreSQL-based pg\_textsearch for BM25 retrieval, integrated Qdrant for dense embedding indexing, adopted the Text Embeddings Interface (TEI) for efficient embedding generation, and developed a new reranker training pipeline. We also explored query expansion via HyDE and a Context-1 LLM-based retrieval strategy. For Phases~A+~and~B, we introduced an LLM-as-a-judge framework and a novel multi-agent quorum mechanism, where agents with diverse prompts debate and converge on a consensus answer using adaptive document retention based on snippet-level evidence. We also extended our participation to the snippet generation subtask for the first time, and revisiting exact answer generation.

This paper is organized as follows. Section~\ref{sec:previous-work} summarizes our system from the previous year and the conclusions that shaped this year's development. Section~\ref{sec:methodology} describes the methodological changes introduced across all pipeline phases, Section~\ref{sec:results} presents our internal validation and official results, Section~\ref{sec:discussion} discusses the lessons learned and directions for future work, and Section~\ref{sec:conclusion} concludes the paper.
