\section{Results}
\label{sec:results}

This section presents both our internal validation results and the official evaluation results for each phase across the four test batches of the 14th BioASQ challenge.

\subsection{Validation}

These experiments were conducted on the 13B Batch~1--2 golden datasets and were designed to measure the marginal contribution of each retrieval component to end-to-end retrieval performance.

\subsubsection{First Stage Retrieval}
\label{sec:internal-retrieval}

We conducted extensive internal testing of the various retrieval strategies introduced this year, including Context-1-based retrieval and different fusion approaches (RRF and weighted sum) with and without neural reranking. Table~\ref{tab:internal-retrieval} presents the results using standard retrieval metrics: M@100 (Match@100, average number of relevant documents in the top 100), H@100 (Hit@100, fraction of questions with $\ge$1 relevant document), AR@100 (AllRel@100, fraction of all relevant documents recovered), MRR (Mean Reciprocal Rank), and R@100 (Recall@100).

\begin{table}[ht]
  \centering
  \caption{Internal retrieval testing results comparing BM25 baseline, fusion strategies of BM25 and dense retrieval (hybrid RRF and weighted sum), reranked variants, and Context-1. Bold values indicate the best result in each column.}
  \label{tab:internal-retrieval}
  \footnotesize
  \footnotesize
  \begin{tabular}{l|cccccc}
    \toprule
    \textbf{Method} & \textbf{Docs} & \textbf{M@100} & \textbf{H@100} & \textbf{AR@100} & \textbf{MRR} & \textbf{R@100} \\
    \midrule
    BM25 (baseline) & 99.3 & 11.01 & 0.953 & 0.082 & 0.549 & 0.373 \\
    \midrule
    Hybrid RRF & 100.0 & 12.28 & 0.965 & 0.047 & 0.696 & 0.406 \\
    Hybrid RRF + BGE-reranker-base & 100.0 & 12.28 & 0.965 & 0.047 & 0.498 & 0.406 \\
    Hybrid RRF + BGE-reranker-v2-m3 & 100.0 & 12.28 & 0.965 & 0.047 & 0.649 & 0.406 \\
    \midrule
    Hybrid weighted sum & 100.0 & 11.47 & 0.965 & 0.082 & 0.622 & 0.384 \\
    Hybrid wsum + BGE-reranker-base & 100.0 & 11.47 & 0.965 & 0.082 & 0.597 & 0.384 \\
    Hybrid wsum + BGE-reranker-v2-m3 & 100.0 & 11.47 & 0.965 & 0.082 & \textbf{0.738} & 0.384 \\
    \midrule
    Context-1 & 100.0 & \textbf{14.16} & 0.965 & 0.047 & 0.508 & \textbf{0.453} \\
    \bottomrule
  \end{tabular}
\end{table}

Several patterns emerge from these results. The BM25 baseline achieves the lowest M@100 (11.01), MRR (0.549), and R@100 (0.373), confirming that lexical retrieval alone is insufficient for this task. Hybrid retrieval, whether fused via RRF or weighted sum, substantially improves over BM25 across all metrics: MRR increases from 0.549 to 0.696 (RRF) and 0.622 (weighted sum), while R@100 rises from 0.373 to 0.406 and 0.384, respectively. RRF consistently outperforms weighted sum on MRR and Recall, consistent with its robustness to heterogeneous score distributions.

The addition of a neural reranker produces mixed but instructive results. When applied to the RRF-fused results, the BGE-reranker-v2-m3 yields an MRR of 0.649, slightly below the un-reranked RRF baseline (0.696), while the base variant drops to 0.498. However, when the reranker is applied to the weighted-sum results, the v2-m3 model achieves the best MRR overall (0.738), suggesting an interaction between the fusion method and the reranker: weighted sum preserves score magnitudes that the reranker can exploit, whereas RRF discards score information in favor of ranks. The base reranker variant consistently underperforms its v2-m3 counterpart, confirming the expected performance hierarchy between these models observed in our validation.

Context-1 achieves the highest M@100 (14.16) and R@100 (0.453), demonstrating its ability to surface a broader set of relevant documents than the single-pass hybrid approaches. However, its MRR (0.508) is lower than the best fusion configurations, indicating that while Context-1 is effective at exploration---finding more relevant documents overall---it is less precise at ranking the most relevant documents first. This is consistent with Context-1's design as a retrieval subagent optimized for recall, intended to feed a downstream reranker or reasoning model rather than to produce a final ranking directly.

\subsubsection{Reranker Models}
\label{sec:internal-validation}

We conducted internal validation of our reranker models using the 13B golden datasets (batches~1--4) as held-out evaluation sets. Performance was measured using the BioASQ-specific MAP metric (MAP@10, based on PubMed article-level relevance judgments). Table~\ref{tab:reranker-val} summarizes the validation results for the top-performing models.

\begin{table}[ht]
  \centering
  \caption{Internal validation results for selected reranker models on the 13B golden datasets.}
  \label{tab:reranker-val}
  \footnotesize
  \begin{tabular}{lcc}
    \toprule
    \textbf{Model} & \textbf{Configuration} & \textbf{MAP-bioasq@10} \\
    \midrule
    LLaMA Nemotron rerank 1B & E2-S4, multi\_neg\_pairwise, InfoNCE & 0.9995 \\
    LLaMA Nemotron rerank 1B & E5, pairwise & 0.9970 \\
    BGE-reranker-v2-m3 & E5, pairwise & 0.6824 \\
    BGE-reranker-base & E5, pairwise & 0.6686 \\
    nboost/pt-biobert-base-msmarco & E5, pairwise & 0.6608 \\
    ncbi/MedCPT-Cross-Encoder & E5, pairwise & 0.6404 \\
    BioLinkBERT-base & E5, pairwise & 0.6403 \\
    cross-encoder/ms-marco-MiniLM-L-6-v2 & E5, pairwise & 0.6373 \\
    PubMedBERT-base & E5, pairwise & 0.6291 \\
    \bottomrule
  \end{tabular}
\end{table}

The LLaMA Nemotron reranker models achieved outstanding validation performance, substantially outperforming all BERT-based architectures. There are however concerns of data leakage due to the unusually high score. Among the smaller models, BGE-reranker-v2-m3 demonstrated the strongest performance, outperforming the model used in previous years (BioLinkBERT-Base), followed by the biomedical domain-specific models. The gap between general-domain and biomedical-specific rerankers was narrower than in previous years, suggesting that larger pretrained models can effectively transfer to biomedical text without extensive domain-specific pretraining.

\subsubsection{Answer Generation}



\subsection{Official Results}
Our systems are labeled \texttt{bioinfo-0} through \texttt{bioinfo-4}, representing different configurations submitted across batches. For each absolute-value table, we also provide the corresponding ranking position within the full competition field (lower rank = better). Systems sharing the same score receive the same rank, and subsequent ranks are skipped accordingly.

\subsubsection{Document Retrieval (Phase A)}
\label{sec:results-phase-a}
The official Phase~A document retrieval results across the four test batches are presented in Table~\ref{tab:phasea-all}. In Batch 1, we utilized BM25+DPRF exclusively for first-stage retrieval. We primarily experimented with new reranker models by first filtering them (bioinfo-0 and bioinfo-1), evaluating the complete set (bioinfo-2), and employing the previous year's rerankers (bioinfo-3). The key takeaway from these runs was that the filtered models performed significantly worse, indicating that the Nemotron models may not be performing as well as initially anticipated. Furthermore, consistent with prior observations, larger model ensembles tended to yield better performance. Additionally, we noted that the 2025 rerankers outperformed the 2026 variants. Upon further investigation, we discovered that this batch suffered from incomplete indexing, with approximately one million missing documents. We believe this omission severely impacted model efficacy and degraded first-stage retrieval performance for this batch, an issue subsequently corrected in Batch 2.

For Batch 2, we began experimenting with hybrid retrieval. Examining runs bioinfo-0, bioinfo-2, and bioinfo-3—where the top-performing rerankers were paired with varying retrievers—we observe that hybrid retrieval using a weighted sum substantially outperforms alternative approaches. Conversely, hybrid Reciprocal Rank Fusion (RRF) underperformed relative to the BM25 baseline. Several factors could account for these outcomes; most notably, these trends may shift following the release of the final official judgments. Alternatively, this pattern may imply that BM25 features carry higher relative importance than dense retrieval in this specific context. However, looking at bioinfo-1 (which incorporated all rerankers), we observed nearly identical performance to our best sysetm, whilst using a BM25-only configuration, whereas bioinfo-3 experienced a performance drop, suggesting a potential processing anomalies within this specific batch.

In Batch 3, we investigated query expansion techniques via bioinfo-1 and bioinfo-2; however, these configurations once again fell short of the established BM25 baseline. We also evaluated the Context-1 model for first-stage retrieval, which yielded negative results. We again observed that the weighted-sum hybrid approach outperformed RRF hybrid retrieval. Unfortunately, the absence of strict control tests prevents us from verifying whether query expansion provided any intrinsic benefits or merely introduced unnecessary computational overhead.

For Batch 4, we maintained a similar submission strategy but replaced the weighted-sum hybrid run with a control RRF hybrid run to benchmark against a HyDE submission. The results indicate that HyDE significantly boosts retrieval effectiveness, marginally outperforming the BM25 baseline in this instance.

Overall, the results this year appear worse than in previous iterations, with our most successful submissions closely mirroring our prior-year architectures. This suggests that either the newly introduced hybrid configurations are less effective, our evaluation baseline is inherently biased toward BM25, or performance metrics will normalize once final ground-truth evaluations are released.

% Hybrid retrieval with RRF fusion (\texttt{bioinfo-2} in B4, \texttt{bioinfo-2} in B3) consistently outperformed BM25-only retrieval when using the same reranker ensemble, confirming the benefit of combining lexical and dense signals at the first stage. However, this advantage depended on batch characteristics: in Batch~2, BM25 + all rerankers (\texttt{bioinfo-1}, MAP 0.1914) outperformed hybrid RRF + all rerankers (\texttt{bioinfo-3}, MAP 0.0718), suggesting that when the reranker ensemble is large enough, the first-stage retrieval method matters less than the reranker coverage. In Batch~3, the BM25 baseline (\texttt{bioinfo-0}) achieved the best MAP (0.1887, rank~7), highlighting that simpler retrieval can be sufficient when combined with strong reranking.

% Context-1-based retrieval showed strong recall but required reranking for precision: in Batch~3, Context-1 + 2025 rerankers (\texttt{bioinfo-3}) and + 2026 rerankers (\texttt{bioinfo-4}) placed 32nd and 35th respectively, well below the hybrid + best reranker configurations. However, in Batch~4, Context-1 + best rerankers (\texttt{bioinfo-3}) matched Context-1 + all rerankers (\texttt{bioinfo-4}) at 28th, and Context-1 + all rerankers (+ HyDE via hybrid) achieved the best result (\texttt{bioinfo-2}, rank~10), demonstrating that Context-1 benefits substantially from larger reranker ensembles and query expansion.

% The effect of ensemble size was mixed. In Batch~1, larger ensembles (46--70 models) achieved top-10 ranks (6th and 8th), while the filtered subset (5--7 models) ranked 25th--28th. In Batch~2, BM25 + all rerankers (29 models, rank~13) dramatically outperformed BM25 + best rerankers (5 models, rank~44), a gap of 31 positions. Conversely, hybrid RRF with best vs.\ all rerankers showed negligible difference (ranks 50 vs.\ 51). In Batch~4, best rerankers (5 models) on hybrid RRF + HyDE achieved rank~10---our best result in that batch---while all rerankers on Context-1 achieved rank~28, tied with best rerankers. These results suggest that ensemble size matters most when the first-stage retrieval is weak (BM25-only) and matters less when the first stage is already strong (hybrid RRF + HyDE).

\todo[inline]{verify every rank, gmeini generated. for every table. for this table verify all N values}

\begin{table}[ht]
  \centering
  \caption{Phase~A document retrieval results across all four Test Batches. Best is the top competitor MAP (rank 1); Median is the median competitor MAP for that batch.}
  \label{tab:phasea-all}
  \footnotesize
  \begin{tabular}{cl|lll|cc}
    \toprule
    \textbf{Batch} & \textbf{System} & \textbf{Retriever} & \textbf{Reranker Ensemble} & \textbf{N} & \textbf{MAP} & \textbf{Rank} \\
    \midrule
    \multirow{7}{*}{1}
    & bioinfo-0 & BM25 & Filtered (MAP$>$0.64) & 5--7 & 0.1476 & 34 \\
    & bioinfo-1 & BM25 + DPRF & Filtered (MAP$>$0.64) & 5--7 & 0.1502 & 30 \\
    & bioinfo-2 & - & All 2026 rerankers & $\sim$24 & 0.2220 & 14 \\
    & bioinfo-3 & - & All 2025 rerankers & $\sim$46 & \textbf{0.2479} & \textbf{5} \\
    & bioinfo-4 & - & All 2025 + 2026 rerankers & $\sim$70 & 0.2398 & 11 \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{3}{l|}{} & 0.2835 & 1 \\
    & \textit{Median} & \multicolumn{3}{l|}{} & 0.1691 & 27 \\
    \midrule
    \multirow{7}{*}{2}
    & bioinfo-0 & BM25 & Best rerankers & $\sim$5 & 0.0813 & 59 \\
    & bioinfo-1 & - & All 2026 rerankers & $\sim$29 & 0.1914 & 15 \\
    & bioinfo-2 & Hybrid RRF & Best rerankers & $\sim$5 & 0.0721 & 60 \\
    & bioinfo-3 &- & All 2026 rerankers & $\sim$29 & 0.0718 & 61 \\
    & bioinfo-4 & Hybrid wsum & Best rerankers & $\sim$5 & \textbf{0.1922} & \textbf{14} \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{3}{l|}{} & 0.2395 & 1 \\
    & \textit{Median} & \multicolumn{3}{l|}{} & 0.1406 & 33--34 \\
    \midrule
    \multirow{7}{*}{3}
    & bioinfo-0 & BM25 & Best rerankers (baseline) & $\sim$5 & \textbf{0.1887} & \textbf{5} \\
    & bioinfo-1 & Hybrid wsum + HyDE & Best rerankers & $\sim$5 & 0.1600 & 17 \\
    & bioinfo-2 & Hybrid RRF + HyDE & Best rerankers & $\sim$5 & 0.1419 & 21 \\
    & bioinfo-3 & Context-1 & 2025 rerankers & $\sim$46 & 0.1088 & 47 \\
    & bioinfo-4 & Context-1 & 2026 rerankers & $\sim$24 & 0.0993 & 49 \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{3}{l|}{} & 0.2114 & 1 \\
    & \textit{Median} & \multicolumn{3}{l|}{} & 0.1253 & 31--32 \\
    \midrule
    \multirow{7}{*}{4}
    & bioinfo-0 & BM25 & Best rerankers (baseline) & $\sim$5 & 0.1951 & 13 \\
    & bioinfo-1 & Hybrid RRF & Best rerankers & $\sim$5 & 0.1163 & 53 \\
    & bioinfo-2 & Hybrid RRF + HyDE & Best rerankers & $\sim$5 & \textbf{0.1959} & \textbf{11} \\
    & bioinfo-3 & Context-1 & Best rerankers & $\sim$5 & 0.1538 & 40 \\
    & bioinfo-4 & Context-1 & All 2026 rerankers & $\sim$24 & 0.1538 & 41 \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{3}{l|}{} & 0.2310 & 1 \\
    & \textit{Median} & \multicolumn{3}{l|}{} & 0.1598 & 38--39 \\
    \bottomrule
  \end{tabular}
\end{table}

% ============================================================
% BATCH 1 PHASE A
% ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase~A document retrieval results for Test Batch~1. Systems explored the effect of reranker ensemble size atop DPRF (Dense Passage Retrieval Fusion). Best competitor MAP: $\sim$0.38, Median MAP: $\sim$0.27.}
%   \label{tab:phasea-b1}
%   \footnotesize
%   \footnotesize\begin{tabular}{lllccccc}
%     \toprule
%     \textbf{System} & \textbf{Retriever} & \textbf{Reranker Ensemble} & \textbf{N} & \textbf{MAP} & \textbf{Rank} & \textbf{Best MAP} & \textbf{Med. MAP} \\
%     \midrule
%     bioinfo-0 & DPRF & Filtered (map@bioasq$>$0.64) & 5--7 & 0.1476 & 28 & $\sim$0.38 & $\sim$0.27 \\
%     bioinfo-1 & DPRF  & Filtered (map@bioasq$>$0.64) & 5--7 & 0.1502 & 25 & $\sim$0.38 & $\sim$0.27 \\
%     bioinfo-2 & DPRF & All 2026 rerankers & $\sim$24 & 0.2220 & 10 & $\sim$0.38 & $\sim$0.27 \\
%     bioinfo-3 & DPRF & All 2025 rerankers & $\sim$46 & \textbf{0.2479} & \textbf{6} & $\sim$0.38 & $\sim$0.27 \\
%     bioinfo-4 & DPRF & All 2025 + 2026 rerankers & $\sim$70 & 0.2398 & 8 & $\sim$0.38 & $\sim$0.27 \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 2 PHASE A
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase~A document retrieval results for Test Batch~2. Systems compared BM25-only vs.\ hybrid (BM25 + dense) retrieval with best or all rerankers. Best competitor MAP: $\sim$0.44, Median MAP: $\sim$0.30.}
%   \label{tab:phasea-b2}
%   \footnotesize
%   \footnotesize\begin{tabular}{lllccccc}
%     \toprule
%     \textbf{System} & \textbf{Retriever} & \textbf{Reranker Ensemble} & \textbf{N} & \textbf{MAP} & \textbf{Rank} & \textbf{Best MAP} & \textbf{Med. MAP} \\
%     \midrule
%     bioinfo-0 & BM25 & Best rerankers & $\sim$5  & 0.0813 & 44 & $\sim$0.44 & $\sim$0.30 \\
%     bioinfo-1 & BM25 & All rerankers & $\sim$29 & 0.1914 & 13 & $\sim$0.44 & $\sim$0.30 \\
%     bioinfo-2 & Hybrid RRF & Best rerankers & $\sim$5  & 0.0721 & 50 & $\sim$0.44 & $\sim$0.30 \\
%     bioinfo-3 & Hybrid RRF & All rerankers & $\sim$29 & 0.0718 & 51 & $\sim$0.44 & $\sim$0.30 \\
%     bioinfo-4 & Hybrid wsum & Best rerankers & $\sim$5  & \textbf{0.1922} & \textbf{12} & $\sim$0.44 & $\sim$0.30 \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 3 PHASE A
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase~A document retrieval results for Test Batch~3. Systems compared BM25 baseline, hybrid + HyDE, and Context-1 with old vs.\ new rerankers. Best competitor MAP: $\sim$0.30, Median MAP: $\sim$0.20.}
%   \label{tab:phasea-b3}
%   \footnotesize
%   \footnotesize\begin{tabular}{lllccccc}
%     \toprule
%     \textbf{System} & \textbf{Retriever} & \textbf{Reranker Ensemble} & \textbf{N} & \textbf{MAP} & \textbf{Rank} & \textbf{Best MAP} & \textbf{Med. MAP} \\
%     \midrule
%     bioinfo-0 & BM25 & Best rerankers (baseline) & $\sim$5  & \textbf{0.1887} & \textbf{7}  & $\sim$0.30 & $\sim$0.20 \\
%     bioinfo-1 & Hybrid wsum + HyDE & Best rerankers & $\sim$5  & 0.1600 & 14 & $\sim$0.30 & $\sim$0.20 \\
%     bioinfo-2 & Hybrid RRF + HyDE & Best rerankers & $\sim$5  & 0.1419 & 19 & $\sim$0.30 & $\sim$0.20 \\
%     bioinfo-3 & Context-1 & 2025 rerankers & $\sim$46 & 0.1088 & 32 & $\sim$0.30 & $\sim$0.20 \\
%     bioinfo-4 & Context-1 & 2026 rerankers & $\sim$24 & 0.0993 & 35 & $\sim$0.30 & $\sim$0.20 \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 4 PHASE A
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase~A document retrieval results for Test Batch~4. Systems compared BM25 baseline, hybrid RRF, HyDE, and Context-1 with best or all rerankers. Best competitor MAP: $\sim$0.17, Median MAP: $\sim$0.06.}
%   \label{tab:phasea-b4}
%   \footnotesize
%   \footnotesize\begin{tabular}{lllccccc}
%     \toprule
%     \textbf{System} & \textbf{Retriever} & \textbf{Reranker Ensemble} & \textbf{N} & \textbf{MAP} & \textbf{Rank} & \textbf{Best MAP} & \textbf{Med. MAP} \\
%     \midrule
%     bioinfo-0 & BM25 & Best rerankers (baseline) & $\sim$5  & 0.1951 & 12 & $\sim$0.17 & $\sim$0.06 \\
%     bioinfo-1 & Hybrid RRF & Best rerankers & $\sim$5  & 0.1163 & 44 & $\sim$0.17 & $\sim$0.06 \\
%     bioinfo-2 & Hybrid RRF + HyDE & Best rerankers & $\sim$5  & \textbf{0.1959} & \textbf{10} & $\sim$0.17 & $\sim$0.06 \\
%     bioinfo-3 & Context-1 & Best rerankers & $\sim$5  & 0.1538 & 28 & $\sim$0.17 & $\sim$0.06 \\
%     bioinfo-4 & Context-1 & All rerankers & $\sim$24 & 0.1538 & 28 & $\sim$0.17 & $\sim$0.06 \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% \paragraph{Phase A Analysis.}

\subsubsection{Snippet Retrieval (Phase A)}
\label{sec:results-snippets}

For the snippet retrieval subtask, we participated starting from Test Batch~3. Table~\ref{tab:snippets} presents the simplified results showing MAP, rank, and the configuration used for each submission. All snippet submissions used the corresponding Phase~A document retrieval pipeline as their document source, with snippet extraction performed by the generation models described in Section~\ref{sec:methodology}.

\begin{table}[ht]
  \centering
  \caption{Snippet retrieval results across test batches. All submissions used the Phase~A retrieval pipeline for document sourcing; snippet extraction was performed by the same generation models used in Phase~A+/B. System ranks are calculated out of all participating systems (50 in B3, 66 in B4).}
  \label{tab:snippets}
  \footnotesize
  \begin{tabular}{lcccc}
    \toprule
    \multirow{2}{*}{\textbf{System}} & \multicolumn{2}{c}{\textbf{Batch B3}} & \multicolumn{2}{c}{\textbf{Batch B4}} \\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    & \textbf{MAP} & \textbf{Rank} & \textbf{MAP} & \textbf{Rank} \\
    \midrule
    bioinfo-0 & \textbf{0.0546} & \textbf{25} & \textbf{0.0591} & \textbf{28} \\
    bioinfo-1 & 0.0352 & 32 & 0.0296 & 51 \\
    bioinfo-2 & 0.0375 & 30 & 0.0495 & 35 \\
    bioinfo-3 & 0.0267 & 38 & 0.0431 & 42 \\
    bioinfo-4 & 0.0130 & 47 & 0.0490 & 36 \\
    \midrule
    \textbf{Best}   & 0.1440 & 1 & 0.1750 & 1 \\
    \textbf{Median} & 0.0543 & 25-26 & 0.0512 & 33-34 \\
    \bottomrule
  \end{tabular}
\end{table}

Snippet retrieval performance was modest, reflecting the difficulty of the task and our first attempt at this subtask. The best MAP ranks were 7th (\texttt{bioinfo-0}, Batch~3) and 17th (\texttt{bioinfo-0}, Batch~4). Interestingly, the BM25 + best rerankers baseline achieved our best snippet rank in both batches, suggesting that snippet extraction benefited from the simpler, higher-precision document retrieval pipeline. Context-1, despite its strong recall for documents, produced lower snippet MAP---consistent with the observation that Context-1 retrieves more documents but with lower precision, making snippet extraction from those documents more challenging.

\subsubsection{Exact Answers (Phases A+ and B)}
\label{sec:results-phase-aplus}

Phase~A+ requires generating exact answers (yes/no, factoid, and list-type questions) as well as ideal answers (paragraph-length summaries). For each batch, we present both the absolute scores and the competition rankings side by side. Each system description indicates the models used for exact answer generation and ideal answer synthesis. The source used for documents in phase A+ is always bioinfo-0 from phase A.

For exact answers we report the official metrics: F1 for yes/no questions,
MRR for factoid questions, and F1 for list questions, in Phase~A+
(Table~\ref{tab:phaseap-exact-all}) and Phase~B (Table~\ref{tab:phaseb-exact-all}).

In Phase~A+, our systems were most competitive on the factoid and list metrics,
while yes/no F1 stayed close to the leaderboard median throughout. In Batch~1 our
submissions clustered around the median, with the proprietary/mixed quorums
(\texttt{bioinfo-1}, \texttt{bioinfo-2}) reaching our best ranks on factoid
(0.3261, rank~13) and list (0.1735, rank~20). Batch~2 showed a clear benefit from
the LLM-as-judge stage: the judge-based runs (\texttt{bioinfo-3}, top-$k$\,=\,1 and
\texttt{bioinfo-4}, top-$k$\,=\,3) lifted list F1 to 0.3145 (rank~15) and 0.3227
(rank~13), well above the plain agent quorums (0.18--0.25), while also leading on
yes/no and factoid. Our strongest batch was Batch~3, where two quorums reached a
perfect yes/no F1 of 1.0 (rank~1): the open-source \texttt{bioinfo-1} and the
mixed-API \texttt{bioinfo-2}. The open-source \texttt{bioinfo-3} quorum placed 3rd
on factoid (0.4706) and 6th on list (0.3138), exceeding the mixed-API
\texttt{bioinfo-2} on both metrics and indicating that an all-open-source quorum was
competitive with proprietary configurations; its yes/no score (0.8952, rank~18) was
above median but below our top systems that batch. In Batch~4, the Mistral quorum
\texttt{bioinfo-4} placed 2nd on factoid (0.3636), and list F1 stayed above median
for the smaller open quorums.

Phase~B follows a similar pattern, with differentiation coming from factoid and list
while yes/no scores sit at or slightly below the median. In Batch~1, both submissions
used the LLM-as-judge pipeline, and widening the judge from top-$k$\,=\,3 to
top-$k$\,=\,5 improved factoid MRR from 0.4130 to 0.4565 (rank~8). Batch~2 again
favoured the judge/ensemble systems: LLM-as-judge with ensemble summarization
(\texttt{bioinfo-3}) gave our best list F1 (0.4366, rank~15), while the Sonnet-4.6
ideal-answer ensemble (\texttt{bioinfo-4}) led on factoid (0.3500, rank~10). In
Batch~3 the Mistral quorum (\texttt{bioinfo-4}) reached 0.5000 factoid MRR (rank~8).
Batch~4 was our strongest Phase~B result: the Qwen quorum (\texttt{bioinfo-3}) placed
5th on factoid (0.5000) and 9th on list (0.5671), and two systems (\texttt{bioinfo-0},
\texttt{bioinfo-4}) reached 3rd on yes/no (0.9352).

Across both phases, yes/no F1 was a poor discriminator---scores were tightly bunched
near the median for almost all participants---whereas factoid and list F1 separated
systems more clearly and accounted for nearly all of our top-10 finishes. Two design
choices recur in our best runs: the LLM-as-judge / ensemble-selection stage, which
gave the largest gains on list F1, and open-source quorums that matched or exceeded
mixed proprietary-API configurations.

\begin{table}[ht]
  \centering
  \caption{Phase~A+ exact answer results across all four Test Batches. Scores are shown with their overall leaderboard ranking in parentheses. The top-performing system among our submissions in each batch is highlighted in bold. \textbf{Best} represents the top competitor score (Rank 1); \textbf{Median} is the median score (and median rank) across all participants for that batch.}
  \label{tab:phaseap-exact-all}
  \footnotesize
  \begin{tabular}{cl|p{5.8cm}|ccc}
    \toprule
    \textbf{Batch} & \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N F1} & \textbf{Fact. MRR} & \textbf{List F1} \\
    \midrule
    \multirow{7}{*}{1}
    & bioinfo-0 & MedGemma-27B + Qwen3.5 35B & 0.8211 (37) & 0.2696 (23) & 0.1509 (28) \\
    & bioinfo-1 & Qwen3.5 235B + Qwen Max Thinking & \textbf{0.8786 (16)} & \textbf{0.3261 (13)} & \textbf{0.1735 (20)} \\
    & bioinfo-2 & Gemini 2.0 Flash + 2.5 Flash + Qwen3.5 122B & \textbf{0.8786 (16)} & \textbf{0.3261 (13)} & 0.1731 (22) \\
    & bioinfo-3 & Gemini 2.0 Flash + 2.5 Flash & \textbf{0.8786 (16)} & 0.2609 (24) & \textbf{0.1735 (20)} \\
    & bioinfo-4 & All models ensemble & \textbf{0.8786 (16)} & 0.2609 (24) & 0.1731 (22) \\
    \cmidrule(l){2-6}
    & \textit{Best} & \multicolumn{1}{l|}{} & 1.0000 (1) & 0.4783 (1) & 0.2345 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.8786 (27) & 0.2761 (27) & 0.1731 (27) \\
    \midrule
    \multirow{7}{*}{2}
    & bioinfo-0 & Agents v1 (3-open-27-120b) & 0.8444 (28) & 0.2000 (39) & 0.1778 (48) \\
    & bioinfo-1 & Agents v2 (5-mixed) & \textbf{0.8929 (10)} & 0.2250 (33) & 0.2479 (29) \\
    & bioinfo-2 & Agents v3 (4-open-35-309b) & 0.8444 (28) & 0.2000 (39) & 0.2306 (36) \\
    & bioinfo-3 & LLM-as-judge top-k=1 & \textbf{0.8929 (10)} & 0.2450 (27) & 0.3145 (15) \\
    & bioinfo-4 & LLM-as-judge top-k=3 & 0.8444 (28) & \textbf{0.2750 (22)} & \textbf{0.3227 (13)} \\
    \cmidrule(l){2-6}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.9481 (1) & 0.4000 (1) & 0.3909 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.8833 (28) & 0.2667 (28) & 0.2544 (28) \\
    \midrule
    \multirow{7}{*}{3}
    & bioinfo-0 & Agents v0 [S] (3-open-2-4b ) & 0.8952 (18) & 0.4118 (9) & 0.2671 (19) \\
    & bioinfo-1 & Agents v1 [M] (4-open-26-35b ) & \textbf{1.0000 (1)} & 0.4118 (9) & 0.2891 (11) \\
    & bioinfo-2 & Agents v2 (5-mixed-api) & \textbf{1.0000 (1)} & 0.3824 (15) & 0.2649 (20) \\
    & bioinfo-3 & Agents v3 (4-open-24-123b) & 0.8952 (18) & \textbf{0.4706 (3)} & \textbf{0.3138 (6)} \\
    & bioinfo-4 & Agents ensemble (v0 + v1 + v2 + v3) & 0.8952 (18) & 0.4412 (6) & 0.2790 (13) \\
    \cmidrule(l){2-6}
    & \textit{Best} & \multicolumn{1}{l|}{} & 1.0000 (1) & 0.5294 (1) & 0.3258 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.8036 (30) & 0.3235 (30) & 0.2449 (30) \\
    \midrule
    \multirow{6}{*}{4}
    & bioinfo-0 & Agents v0 [S] (3-open-2-4b ) & \textbf{0.8667 (11)} & 0.2727 (14) & 0.2316 (40) \\
    & bioinfo-1 & Agents v1 (2-gemma-4-26-31b ) & \textbf{0.8667 (11)} & 0.2727 (14) & 0.3133 (24) \\
    & bioinfo-3 & Agents v3 (3-qwen-mixed-27-35b) & \textbf{0.8667 (11)} & 0.2727 (14) & \textbf{0.3388 (19)} \\
    & bioinfo-4 & Agents v4 (3-mistral-129-695b) & \textbf{0.8667 (11)} & \textbf{0.3636 (2)} & 0.2047 (45) \\
    \cmidrule(l){2-6}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.9352 (1) & 0.4091 (1) & 0.4840 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.8667 (28) & 0.2273 (28) & 0.3065 (28) \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[ht]
  \centering
  \caption{Phase~B exact answer results across all four Test Batches. Scores are shown with their overall leaderboard ranking in parentheses. The top-performing system among our submissions in each batch is highlighted in bold. \textbf{Best} represents the top competitor score (Rank 1); \textbf{Median} is the median score (and median rank) across all participants for that batch.}
  \label{tab:phaseb-exact-all}
  \footnotesize
  \begin{tabular}{cl|p{5.5cm}|ccc}
    \toprule
    \textbf{Batch} & \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N F1} & \textbf{Fact. MRR} & \textbf{List F1} \\
    \midrule
    \multirow{4}{*}{1}
    & bioinfo-0 & LLM-as-judge top-k=3 & \textbf{0.8786 (24)} & 0.4130 (23) & 0.2581 (33) \\
    & bioinfo-1 & LLM-as-judge top-k=5 & \textbf{0.8786 (24)} & \textbf{0.4565 (8)} & \textbf{0.2659 (28)} \\
    \cmidrule(l){2-6}
    & \textit{Best} & \multicolumn{1}{l|}{} & 1.0000 (1) & 0.5217 (1) & 0.3613 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.9377 (21) & 0.4203 (21) & 0.2443 (21) \\
    \midrule
    \multirow{7}{*}{2}
    & bioinfo-0 & Agents v1 (3-open-27-120b) & 0.8518 (35) & 0.2500 (39) & 0.3836 (28) \\
    & bioinfo-1 & Agents v2 (5-mixed) & \textbf{0.8929 (9)} & 0.3250 (20) & 0.2270 (43) \\
    & bioinfo-2 & Agents v4 [S] (3-gemma-27-31b) & \textbf{0.8929 (9)} & 0.3000 (23) & 0.3709 (30) \\
    & bioinfo-3 & LLM-as-judge + ensemble summarization (mixed) & \textbf{0.8929 (9)} & 0.3000 (23) & \textbf{0.4366 (15)} \\
    & bioinfo-4 & Ensemble (Gemini + Nemotron) exact + Sonnet 4.6 ideal & 0.8518 (35) & \textbf{0.3500 (10)} & 0.4062 (23) \\
    \cmidrule(l){2-6}
    & \textit{Best} & \multicolumn{1}{l|}{} & 1.0000 (1) & 0.4259 (1) & 0.4720 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.8929 (25) & 0.3250 (25) & 0.3921 (25) \\
    \midrule
    \multirow{7}{*}{3}
    & bioinfo-0 & Agents v0 [S] (3-open-2-4b) & \textbf{0.8952 (12)} & 0.3824 (26) & \textbf{0.4102 (22)} \\
    & bioinfo-1 & Agents v1 [M] (4-open-26-35b) & \textbf{0.8952 (12)} & 0.4706 (14) & 0.3575 (33) \\
    & bioinfo-2 & Agents v2 (5-mixed) & \textbf{0.8952 (12)} & 0.3725 (28) & 0.3963 (26) \\
    & bioinfo-3 & Agents v3 (4-open-24-123b) & 0.8036 (38) & 0.3824 (26) & 0.4053 (24) \\
    & bioinfo-4 & Agents v4 (3-mistral-129-695b) & \textbf{0.8952 (12)} & \textbf{0.5000 (8)} & 0.3763 (31) \\
    \cmidrule(l){2-6}
    & \textit{Best} & \multicolumn{1}{l|}{} & 1.0000 (1) & 0.5882 (1) & 0.5175 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.8952 (23) & 0.4412 (23) & 0.3963 (23) \\
    \midrule
    \multirow{7}{*}{4}
    & bioinfo-0 & Agents v0 [S] (3-open-2-4b) & \textbf{0.9352 (3)} & 0.3182 (26) & 0.3809 (36) \\
    & bioinfo-1 & Agents v1 (2-gemma-4-26-31b) & 0.8667 (19) & 0.2273 (38) & 0.4858 (24) \\
    & bioinfo-2 & Agents v2 (4-mixed-b4) & 0.8667 (19) & 0.4091 (10) & 0.4763 (26) \\
    & bioinfo-3 & Agents v3 (3-qwen-mixed-27-35b) & 0.8667 (19) & \textbf{0.5000 (5)} & \textbf{0.5671 (9)} \\
    & bioinfo-4 & Agents v5 (2-mistral-129-695b) & \textbf{0.9352 (3)} & 0.3939 (16) & 0.3862 (34) \\
    \cmidrule(l){2-6}
    & \textit{Best} & \multicolumn{1}{l|}{} & 1.0000 (1) & 0.5758 (1) & 0.6543 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.8667 (24) & 0.3182 (24) & 0.4858 (24) \\
    \bottomrule
  \end{tabular}
\end{table}

% % ============================================================
% % BATCH 1 PHASE A+
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase A+ exact answer scores and rankings for Test Batch~1. Rankings shown in parentheses. Base retrieval: DPRF + Rerankers $>$0.64.}
%   \label{tab:phaseap-b1}
%   \footnotesize
%   \resizebox{\textwidth}{!}{\footnotesize\begin{tabular}{lp{5.5cm}cccccccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Models (Exact / Ideal)} & \textbf{Y/N Acc.} & \textbf{Y/N F1} & \textbf{Fact. S.} & \textbf{Fact. L.} & \textbf{Fact. MRR} & \textbf{List P.} & \textbf{List R.} & \textbf{List F1} \\
%     \midrule
%     bioinfo-0 & MedGemma-27B + Qwen3.5 35B / Nemotron-3-Super-120B & 0.8235 (36) & 0.8211 (31) & 0.2609 (26) & 0.3043 (30) & 0.2696 (32) & 0.1275 (35) & 0.2219 (26) & 0.1509 (35) \\
%     bioinfo-1 & Qwen3.5 235B + Qwen Max Thinking / Nemotron-3-Super-120B & 0.8824 (14) & 0.8786 (22) & 0.3043 (14) & 0.3478 (19) & 0.3261 (18) & 0.1461 (24) & 0.2485 (15) & 0.1735 (24) \\
%     bioinfo-2 & Gemini 2.0 Flash + 2.5 Flash + Qwen3.5 122B / Opus + Sonnet & 0.8824 (14) & 0.8786 (22) & 0.3043 (14) & 0.3478 (19) & 0.3261 (18) & 0.1534 (22) & 0.2334 (23) & 0.1731 (25) \\
%     bioinfo-3 & Gemini 2.0 Flash + 2.5 Flash / Opus + Sonnet & 0.8824 (14) & 0.8786 (22) & 0.2609 (26) & 0.2609 (39) & 0.2609 (35) & 0.1461 (24) & 0.2485 (15) & 0.1735 (24) \\
%     bioinfo-4 & All models ensemble / Opus + Sonnet & 0.8824 (14) & 0.8786 (22) & 0.2609 (26) & 0.2609 (39) & 0.2609 (35) & 0.1534 (22) & 0.2334 (23) & 0.1731 (25) \\
%     \bottomrule
%   \end{tabular}
% }%
%   \par\medskip
%   \caption{Phase A+ ideal answer scores and rankings for Test Batch~1. Rankings shown in parentheses.}
%   \label{tab:phaseap-b1-ideal}
%   \footnotesize\begin{tabular}{llcccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Models} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
%     \midrule
%     bioinfo-2 & Opus + Sonnet & 0.2408 (7) & 0.0825 (32) & 0.2706 (7) & 0.0932 (34) \\
%     bioinfo-4 & Opus + Sonnet & 0.2348 (11) & 0.0916 (29) & 0.2664 (8) & 0.1023 (28) \\
%     bioinfo-3 & Opus + Sonnet & 0.2245 (16) & 0.0955 (26) & 0.2489 (15) & 0.1021 (29) \\
%     bioinfo-1 & Nemotron-3-Super-120B & 0.2200 (17) & 0.1009 (22) & 0.2393 (18) & 0.1074 (24) \\
%     bioinfo-0 & Nemotron-3-Super-120B & 0.2150 (21) & 0.1021 (21) & 0.2340 (20) & 0.1094 (22) \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 2 PHASE A+
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase A+ exact answer scores and rankings for Test Batch~2. Rankings shown in parentheses. Systems used agent-based generation with different model configurations.}
%   \label{tab:phaseap-b2}
%   \footnotesize
%   \resizebox{\textwidth}{!}{\footnotesize\begin{tabular}{lp{5.5cm}cccccccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N Acc.} & \textbf{Y/N F1} & \textbf{Fact. S.} & \textbf{Fact. L.} & \textbf{Fact. MRR} & \textbf{List P.} & \textbf{List R.} & \textbf{List F1} \\
%     \midrule
%     bioinfo-0 & Agents v1 (3-open-27-120b) & 0.8571 (27) & 0.8444 (25) & 0.2000 (30) & 0.2000 (45) & 0.2000 (40) & 0.2401 (23) & 0.1608 (50) & 0.1778 (48) \\
%     bioinfo-1 & Agents v2 (5-mixed) & 0.9048 (9) & 0.8929 (12) & 0.2000 (30) & 0.2500 (35) & 0.2250 (33) & 0.2391 (24) & 0.2784 (23) & 0.2479 (26) \\
%     bioinfo-2 & Agents v3 (4-open-35-309b) & 0.8571 (27) & 0.8444 (25) & 0.2000 (30) & 0.2000 (45) & 0.2000 (40) & 0.2406 (22) & 0.2249 (44) & 0.2306 (39) \\
%     bioinfo-3 & LLM-as-judge top-k=1 & 0.9048 (9) & 0.8929 (12) & 0.2000 (30) & 0.3500 (14) & 0.2450 (27) & 0.2926 (12) & 0.3841 (7) & 0.3145 (9) \\
%     bioinfo-4 & LLM-as-judge top-k=3 & 0.8571 (27) & 0.8444 (25) & 0.2500 (23) & 0.3000 (28) & 0.2750 (26) & 0.2948 (11) & 0.4034 (5) & 0.3227 (8) \\
%     \bottomrule
%   \end{tabular}
% }%
%   \par\medskip
%   \caption{Phase A+ ideal answer scores and rankings for Test Batch~2. Rankings shown in parentheses.}
%   \label{tab:phaseap-b2-ideal}
%   \footnotesize\begin{tabular}{llcccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
%     \midrule
%     bioinfo-3 & LLM-as-judge top-k=1 & 0.2843 (3) & 0.0983 (35) & 0.2984 (3) & 0.1082 (35) \\
%     bioinfo-4 & LLM-as-judge top-k=3 & 0.2833 (4) & 0.0963 (36) & 0.2983 (4) & 0.1061 (36) \\
%     bioinfo-1 & Agents v2 & 0.2280 (17) & 0.1236 (18) & 0.2406 (19) & 0.1291 (20) \\
%     bioinfo-0 & Agents v1 & 0.1892 (39) & 0.1322 (13) & 0.1966 (40) & 0.1334 (13) \\
%     bioinfo-2 & Agents v3 & 0.1755 (45) & 0.1286 (22) & 0.1918 (43) & 0.1353 (12) \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 3 PHASE A+
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase A+ exact answer scores and rankings for Test Batch~3. Rankings shown in parentheses. Base retrieval: Context-1 + new rerankers. \textbf{[S]} = small/lightweight local models.}
%   \label{tab:phaseap-b3}
%   \footnotesize
%   \resizebox{\textwidth}{!}{\footnotesize\begin{tabular}{lp{5.5cm}cccccccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N Acc.} & \textbf{Y/N F1} & \textbf{Fact. S.} & \textbf{Fact. L.} & \textbf{Fact. MRR} & \textbf{List P.} & \textbf{List R.} & \textbf{List F1} \\
%     \midrule
%     bioinfo-0 & Agents v0 [S] (3-open-2-4b) & 0.9091 (28) & 0.8952 (23) & 0.4118 (1) & 0.4118 (26) & 0.4118 (9) & 0.2835 (10) & 0.2659 (28) & 0.2671 (20) \\
%     bioinfo-1 & Agents v1 [M] (4-open-26-35b) & 1.0000 (1) & 1.0000 (1) & 0.3529 (6) & 0.4706 (9) & 0.4118 (9) & 0.2787 (11) & 0.3355 (9) & 0.2891 (11) \\
%     bioinfo-2 & Agents v2 (5-mixed) & 1.0000 (1) & 1.0000 (1) & 0.2941 (16) & 0.4706 (9) & 0.3824 (15) & 0.2459 (19) & 0.3221 (13) & 0.2649 (17) \\
%     bioinfo-3 & Agents v3 (4-open-24-123b) & 0.9091 (28) & 0.8952 (23) & 0.4118 (1) & 0.5294 (2) & 0.4706 (2) & 0.2863 (9) & 0.3779 (4) & 0.3138 (6) \\
%     bioinfo-4 & Agents ensemble (v0 + v1 + v2 + v3) & 0.9091 (28) & 0.8952 (23) & 0.3529 (6) & 0.5294 (2) & 0.4412 (5) & 0.2602 (15) & 0.3140 (14) & 0.2790 (13) \\
%     \bottomrule
%   \end{tabular}
% }%
%   \par\medskip
%   \caption{Phase A+ ideal answer scores and rankings for Test Batch~3. Rankings shown in parentheses.}
%   \label{tab:phaseap-b3-ideal}
%   \footnotesize\begin{tabular}{llcccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
%     \midrule
%     bioinfo-3 & Agents v3 & 0.2052 (7) & 0.1210 (25) & 0.2192 (7) & 0.1286 (17) \\
%     bioinfo-1 & Agents v1 [M] & 0.1984 (11) & 0.1166 (28) & 0.2135 (12) & 0.1243 (23) \\
%     bioinfo-4 & Agents ensemble & 0.1942 (13) & 0.1223 (23) & 0.2059 (14) & 0.1288 (18) \\
%     bioinfo-2 & Agents v2 & 0.1933 (14) & 0.1203 (26) & 0.2005 (15) & 0.1228 (26) \\
%     bioinfo-0 & Agents v0 [S] & 0.1710 (24) & 0.1201 (27) & 0.1815 (24) & 0.1266 (20) \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 4 PHASE A+
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase A+ exact answer scores and rankings for Test Batch~4. Rankings shown in parentheses. Base retrieval: Context-1 + best rerankers. \textbf{[S]} = small/lightweight local models. \texttt{bioinfo-2} had no submission this batch.}
%   \label{tab:phaseap-b4}
%   \footnotesize
%   \resizebox{\textwidth}{!}{\footnotesize\begin{tabular}{lp{5.5cm}cccccccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N Acc.} & \textbf{Y/N F1} & \textbf{Fact. S.} & \textbf{Fact. L.} & \textbf{Fact. MRR} & \textbf{List P.} & \textbf{List R.} & \textbf{List F1} \\
%     \midrule
%     bioinfo-0 & Agents v0 [S] (3-open-2-4b) & 0.8750 (10) & 0.8667 (12) & 0.2727 (16) & 0.2727 (32) & 0.2727 (26) & 0.2317 (32) & 0.2812 (29) & 0.2316 (33) \\
%     bioinfo-1 & Agents v1 (2-gemma-4-26-31b) & 0.8750 (10) & 0.8667 (12) & 0.2727 (16) & 0.2727 (32) & 0.2727 (26) & 0.3059 (18) & 0.3630 (14) & 0.3133 (18) \\
%     bioinfo-3 & Agents v3 (3-qwen-mixed-27-35b) & 0.8750 (10) & 0.8667 (12) & 0.2727 (16) & 0.2727 (32) & 0.2727 (26) & 0.3196 (16) & 0.4053 (9) & 0.3388 (14) \\
%     bioinfo-4 & Agents v4 (3-mistral-129-695b) & 0.8750 (10) & 0.8667 (12) & 0.3636 (5) & 0.3636 (13) & 0.3636 (12) & 0.2211 (35) & 0.2124 (43) & 0.2047 (42) \\
%     \bottomrule
%   \end{tabular}
% }%
%   \par\medskip
%   \caption{Phase A+ ideal answer scores and rankings for Test Batch~4. Rankings shown in parentheses.}
%   \label{tab:phaseap-b4-ideal}
%   \footnotesize\begin{tabular}{llcccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
%     \midrule
%     bioinfo-1 & Agents v1 & 0.2122 (13) & 0.1152 (35) & 0.2230 (11) & 0.1194 (34) \\
%     bioinfo-3 & Agents v3 & 0.2099 (15) & 0.1220 (27) & 0.2344 (8) & 0.1323 (26) \\
%     bioinfo-4 & Agents v4 & 0.2097 (16) & 0.1151 (37) & 0.2203 (17) & 0.1180 (39) \\
%     bioinfo-0 & Agents v0 [S] & 0.1992 (20) & 0.1213 (29) & 0.2119 (16) & 0.1274 (28) \\
%     \bottomrule
%   \end{tabular}
% \end{table}

\paragraph{Phase A+ Analysis.}
Yes/No accuracy was consistently high across all batches, with perfect scores (1.0000, rank~1) achieved in Batch~3 by \texttt{bioinfo-1} (Agents v1, medium models) and \texttt{bioinfo-2} (Agents v2, large proprietary models). Factoid performance showed greater variability: our best strict accuracy ranks were 1st (\texttt{bioinfo-0} Agents v0 [S] and \texttt{bioinfo-3} Agents v3, both in Batch~3), demonstrating that small model agents can achieve top-tier factoid precision when paired with strong retrieval (Context-1 + new rerankers).

\textbf{Small model competitiveness.} A clear finding was that small model agents (Agents v0, using Gemma-4-E2B/E4B and Nemotron-3-Nano-4B, marked [S] in the tables) performed competitively with much larger configurations. In Batch~3 Phase~A+, Agents v0 [S] achieved 1st in factoid strict accuracy (0.4118), tied with Agents v3, and placed 10th in list precision---outperforming Agents v2 (large proprietary models) which ranked 19th. In Batch~4, Agents v0 [S] achieved identical Y/N accuracy (0.8750, rank~10) and factoid scores (0.2727, rank~16) to Agents v1 (medium models) and Agents v3 (Qwen3.6 family). On ideal answers, Agents v0 [S] achieved R-SU4 F1 of 0.1274 (rank~28) in Batch~4, comparable to Agents v1 (0.1194, rank~34) and Agents v3 (0.1323, rank~26). These results indicate that lightweight local models, when embedded in an agent loop with iterative task solving, can approach the performance of models 10--100$\times$ their parameter count.

\textbf{Agent-based generation.} Multi-model agent configurations (Agents v1--v4) consistently produced strong list-type results: Agents v3 achieved 6th in list F-Measure (Batch~3) and 14th (Batch~4), while Agents v2 achieved 9th (Batch~2). The LLM-as-judge approach (Batch~2, \texttt{bioinfo-3} top-k=1 and \texttt{bioinfo-4} top-k=3) produced excellent list recall (ranks 7 and 5 respectively) and ideal answer recall (ranks 3 and 4), but lower precision/F1, consistent with a recall-oriented selection strategy. The agents ensemble (\texttt{bioinfo-4} in Batch~3) did not outperform the best individual agent (Agents v3), suggesting that ensemble proliferation adds cost without proportional benefit when a well-tuned single agent is available.

\textbf{Cost considerations.} The quorum-based agent architecture, while effective, is computationally expensive: each agent invocation spawns 3--5 parallel model calls plus a synthesis step. For Batch~3, the full agents ensemble (v0+v1+v2+v3) required $\sim$17 model calls per question. The small model agents (v0) required only 4 calls with models runnable on consumer GPUs, representing a $\sim$10$\times$ cost reduction. In many practical scenarios, lightweight agents offer a favorable cost-performance trade-off, particularly for high-throughput or resource-constrained deployment.

\subsubsection{Ideal Answers (Phases A+ and B)}
\label{sec:results-ideal}

For ideal answers we report the official ROUGE-based metrics: ROUGE-2 and ROUGE-SU4,
each reported as recall and F1. Phase~A+ uses system-retrieved documents, while
Phase~B uses gold-standard documents and snippets provided by the organizers,
isolating generation quality from retrieval quality.
Tables~\ref{tab:phaseap-ideal-all} and~\ref{tab:phaseb-ideal-all} present
consolidated results across all four batches.

In Phase~A+ (Table~\ref{tab:phaseap-ideal-all}), recall was consistently our
stronger dimension: our best ROUGE-2 recall ranks were 7th (Batch~1,
\texttt{bioinfo-2}, Opus+Sonnet) and 3rd (Batch~2, \texttt{bioinfo-3},
LLM-as-judge top-$k$\,=\,1). The LLM-as-judge approach dominated Batch~2 ideal
answers, achieving ranks~3 and~4 on both recall metrics, substantially ahead of
the agent quorum configurations (ranks 17--48). However, F1 scores for the
judge-based systems were among the lowest (0.0963--0.0983, ranks~49--51),
indicating that while these answers captured relevant content, they were verbose
and penalized by precision-oriented metrics. In later batches where agent quorums
were used exclusively, recall ranks settled in the 7--15 range for our best
systems, with Agents~v3 consistently leading. Small model agents (v0 [S])
achieved competitive ROUGE-2 F1 ranks of 21st (Batch~3) and 30th (Batch~4),
again demonstrating that lightweight configurations can produce coherent ideal
answers at a fraction of the computational cost. The agents ensemble
(\texttt{bioinfo-4}, Batch~3) achieved our best ideal answer F1 in that batch
(0.1223, 0.1288), suggesting that diversity of perspectives benefits
summarization quality more than it does exact answer precision.

Phase~B ideal answers (Table~\ref{tab:phaseb-ideal-all}) follow similar patterns
but with higher absolute scores due to gold-standard input. The LLM-as-judge
pipeline in Batch~1 produced ranks~13--14 on recall, with top-$k$\,=\,3
outperforming top-$k$\,=\,5 on both recall and F1. In Batch~2, the
LLM-as-judge with ensemble summarization (\texttt{bioinfo-3}) achieved our best
Phase~B ideal recall (0.3386, rank~4), while the lightweight Agents~v4~[S]
(\texttt{bioinfo-2}) produced the strongest F1 (0.1903, rank~16). In Batches~3
and~4, agent quorums dominated and the pattern from Phase~A+ recurred: Agents~v3
led on recall (ranks~8 and 17), while Agents~v0~[S] matched or exceeded larger
configurations on F1 (ranks~11 and~20). Across both phases, ROUGE-based metrics
strongly favor recall over precision for our systems---a direct consequence of
the agent quorum's multi-perspective debate producing comprehensive but sometimes
verbose answers. As noted in previous editions, ROUGE scores correlate imperfectly
with human judgment, and our qualitative assessment suggests that the quorum's
ideal answers were often more informative than their F1 scores imply.
\begin{table}[ht]
  \centering
  \caption{Phase~A+ ideal answer results across all four Test Batches. Scores are shown with their overall leaderboard ranking in parentheses. The top-performing system among our submissions in each batch is highlighted in bold. \textbf{Best} represents the top competitor score (Rank 1); \textbf{Median} is the median score (and median rank) across all participants for that batch.}
  \label{tab:phaseap-ideal-all}
  \footnotesize
  \begin{tabular}{cl|l|cccc}
    \toprule
    \textbf{Batch} & \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
    \midrule
    \multirow{7}{*}{1}
    & bioinfo-0 & Nemotron-3-Super-120B & 0.2150 (21) & \textbf{0.1021 (35)} & 0.2340 (18) & \textbf{0.1094 (33)} \\
    & bioinfo-1 & Nemotron-3-Super-120B & 0.2200 (17) & 0.1009 (36) & 0.2393 (17) & 0.1074 (36) \\
    & bioinfo-2 & Opus + Sonnet & \textbf{0.2408 (7)} & 0.0825 (48) & \textbf{0.2706 (6)} & 0.0932 (48) \\
    & bioinfo-3 & Opus + Sonnet & 0.2245 (16) & 0.0955 (41) & 0.2489 (15) & 0.1021 (40) \\
    & bioinfo-4 & Opus + Sonnet & 0.2348 (11) & 0.0916 (44) & 0.2664 (8) & 0.1023 (39) \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.2725 (1) & 0.1767 (1) & 0.2949 (1) & 0.1821 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.1937 (27) & 0.1206 (27) & 0.2023 (27) & 0.1294 (27) \\
    \midrule
    \multirow{7}{*}{2}
    & bioinfo-0 & Agents v1 & 0.1892 (42) & \textbf{0.1322 (22)} & 0.1966 (42) & 0.1334 (26) \\
    & bioinfo-1 & Agents v2 & 0.2280 (17) & 0.1236 (29) & 0.2406 (19) & 0.1291 (30) \\
    & bioinfo-2 & Agents v3 & 0.1755 (48) & 0.1286 (26) & 0.1918 (45) & \textbf{0.1353 (24)} \\
    & bioinfo-3 & LLM-as-judge top-k=1 & \textbf{0.2843 (3)} & 0.0983 (49) & \textbf{0.2984 (3)} & 0.1082 (49) \\
    & bioinfo-4 & LLM-as-judge top-k=3 & 0.2833 (4) & 0.0963 (51) & 0.2983 (4) & 0.1061 (52) \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.2989 (1) & 0.1839 (1) & 0.3119 (1) & 0.1851 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.2057 (28) & 0.1287 (28) & 0.2187 (28) & 0.1334 (28) \\
    \midrule
    \multirow{7}{*}{3}
    & bioinfo-0 & Agents v0 [S] & 0.1710 (25) & 0.1201 (21) & 0.1815 (27) & 0.1266 (25) \\
    & bioinfo-1 & Agents v1 [M] & 0.1984 (11) & 0.1166 (27) & 0.2135 (11) & 0.1243 (28) \\
    & bioinfo-2 & Agents v2 & 0.1933 (14) & 0.1203 (20) & 0.2005 (19) & 0.1228 (31) \\
    & bioinfo-3 & Agents v3 & \textbf{0.2052 (7)} & 0.1210 (19) & \textbf{0.2192 (8)} & 0.1286 (22) \\
    & bioinfo-4 & Agents ensemble & 0.1942 (13) & \textbf{0.1223 (17)} & 0.2059 (14) & \textbf{0.1288 (21)} \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.2373 (1) & 0.1577 (1) & 0.2682 (1) & 0.1537 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.1609 (30) & 0.1148 (30) & 0.1677 (30) & 0.1220 (30) \\
    \midrule
    \multirow{6}{*}{4}
    & bioinfo-0 & Agents v0 [S] & 0.1992 (21) & 0.1213 (30) & 0.2119 (20) & 0.1274 (31) \\
    & bioinfo-1 & Agents v1 & \textbf{0.2122 (13)} & 0.1152 (38) & 0.2230 (14) & 0.1194 (37) \\
    & bioinfo-3 & Agents v3 & 0.2099 (15) & \textbf{0.1220 (29)} & \textbf{0.2344 (9)} & \textbf{0.1323 (27)} \\
    & bioinfo-4 & Agents v4 & 0.2097 (16) & 0.1151 (39) & 0.2203 (15) & 0.1180 (39) \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.2439 (1) & 0.1714 (1) & 0.2682 (1) & 0.1699 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.1836 (28) & 0.1227 (28) & 0.1951 (28) & 0.1319 (28) \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[ht]
  \centering
  \caption{Phase~B ideal answer results across all four Test Batches. Scores are shown with their overall leaderboard ranking in parentheses. The top-performing system among our submissions in each batch is highlighted in bold. \textbf{Best} represents the top competitor score (Rank 1); \textbf{Median} is the median score (and median rank) across all participants for that batch.}
  \label{tab:phaseb-ideal-all}
  \footnotesize
  \begin{tabular}{cl|p{5.5cm}|cccc}
    \toprule
    \textbf{Batch} & \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
    \midrule
    \multirow{4}{*}{1}
    & bioinfo-0 & LLM-as-judge top-k=3 & \textbf{0.2857 (13)} & \textbf{0.1303 (39)} & \textbf{0.3033 (14)} & \textbf{0.1323 (38)} \\
    & bioinfo-1 & LLM-as-judge top-k=5 & 0.2678 (20) & 0.0958 (55) & 0.2805 (21) & 0.0982 (55) \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.3746 (1) & 0.2487 (1) & 0.3835 (1) & 0.2381 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.2470 (33) & 0.1645 (33) & 0.2517 (33) & 0.1669 (33) \\
    \midrule
    \multirow{7}{*}{2}
    & bioinfo-0 & Agents v1 & 0.2359 (34) & 0.1766 (23) & 0.2328 (34) & 0.1704 (23) \\
    & bioinfo-1 & Agents v2 & 0.2852 (12) & 0.1527 (36) & 0.2848 (12) & 0.1522 (35) \\
    & bioinfo-2 & Agents v4 [S] & 0.3005 (8) & \textbf{0.1903 (16)} & 0.2899 (9) & \textbf{0.1807 (18)} \\
    & bioinfo-3 & LLM-as-judge + ensemble summarization & \textbf{0.3386 (4)} & 0.1334 (46) & \textbf{0.3550 (4)} & 0.1403 (43) \\
    & bioinfo-4 & Ensemble exact + Sonnet 4.6 ideal & 0.3024 (7) & 0.1595 (30) & 0.3022 (7) & 0.1566 (30) \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.4028 (1) & 0.2562 (1) & 0.4155 (1) & 0.2485 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.2586 (33) & 0.1807 (33) & 0.2491 (33) & 0.1795 (33) \\
    \midrule
    \multirow{7}{*}{3}
    & bioinfo-0 & Agents v0 [S] & 0.2472 (20) & \textbf{0.1815 (11)} & 0.2438 (20) & \textbf{0.1774 (11)} \\
    & bioinfo-1 & Agents v1 [M] & 0.2495 (15) & 0.1700 (23) & 0.2464 (18) & 0.1651 (23) \\
    & bioinfo-2 & Agents v2 & 0.2368 (26) & 0.1680 (25) & 0.2402 (26) & 0.1701 (21) \\
    & bioinfo-3 & Agents v3 & \textbf{0.2734 (8)} & 0.1732 (18) & \textbf{0.2704 (8)} & 0.1716 (19) \\
    & bioinfo-4 & Agents v4 & 0.2487 (17) & 0.1661 (28) & 0.2570 (14) & 0.1678 (24) \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.4028 (1) & 0.2607 (1) & 0.4155 (1) & 0.2547 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.2293 (33) & 0.1598 (33) & 0.2265 (33) & 0.1621 (33) \\
    \midrule
    \multirow{7}{*}{4}
    & bioinfo-0 & Agents v0 [S] & 0.2472 (27) & \textbf{0.1742 (20)} & 0.2480 (24) & \textbf{0.1729 (19)} \\
    & bioinfo-1 & Agents v1 & \textbf{0.2716 (15)} & 0.1566 (31) & 0.2678 (15) & 0.1543 (32) \\
    & bioinfo-2 & Agents v2 & 0.2682 (17) & 0.1714 (22) & \textbf{0.2698 (17)} & 0.1698 (22) \\
    & bioinfo-3 & Agents v3 & 0.2401 (30) & 0.1452 (42) & 0.2484 (23) & 0.1467 (41) \\
    & bioinfo-4 & Agents v5 & 0.2496 (26) & 0.1526 (36) & 0.2477 (25) & 0.1496 (36) \\
    \cmidrule(l){2-7}
    & \textit{Best} & \multicolumn{1}{l|}{} & 0.3743 (1) & 0.2827 (1) & 0.3798 (1) & 0.2699 (1) \\
    & \textit{Median}& \multicolumn{1}{l|}{} & 0.2210 (35) & 0.1537 (35) & 0.2102 (35) & 0.1514 (35) \\
    \bottomrule
  \end{tabular}
\end{table}

% % ============================================================
% % BATCH 1 PHASE B
% % ============================================================

% \begin{table}[ht]
%   \centering
%   \caption{Phase B exact answer scores and rankings for Test Batch~1. Rankings shown in parentheses. Both submissions used LLM-as-judge with top-k document selection.}
%   \label{tab:phaseb-b1}
%   \footnotesize
%   \resizebox{\textwidth}{!}{\footnotesize\begin{tabular}{lp{5.5cm}ccccccccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N Acc.} & \textbf{F1 Yes} & \textbf{F1 No} & \textbf{Y/N M-F1} & \textbf{Fact. S.} & \textbf{Fact. L.} & \textbf{F. MRR} & \textbf{List P.} & \textbf{List F1} \\
%     \midrule
%     bioinfo-0 & LLM-as-judge top-k=3 & 0.8824 (32) & 0.9000 (30) & 0.8571 (20) & 0.8786 (26) & 0.3913 (17) & 0.4348 (19) & 0.4130 (18) & 0.2351 (38) & 0.2581 (32) \\
%     bioinfo-1 & LLM-as-judge top-k=5 & 0.8824 (32) & 0.9000 (30) & 0.8571 (20) & 0.8786 (26) & 0.4348 (9) & 0.4783 (10) & 0.4565 (8) & 0.2417 (35) & 0.2659 (29) \\
%     \bottomrule
%   \end{tabular}
% }%
%   \par\medskip
%   \caption{Phase B ideal answer scores and rankings for Test Batch~1. Rankings shown in parentheses.}
%   \label{tab:phaseb-b1-ideal}
%   \footnotesize\begin{tabular}{llcccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
%     \midrule
%     bioinfo-0 & LLM-as-judge top-k=3 & 0.2857 (13) & 0.1303 (39) & 0.3033 (14) & 0.1323 (38) \\
%     bioinfo-1 & LLM-as-judge top-k=5 & 0.2678 (20) & 0.0958 (48) & 0.2805 (21) & 0.0982 (48) \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 2 PHASE B
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase B exact answer scores and rankings for Test Batch~2. Rankings shown in parentheses. \textbf{[S]} = small/lightweight local models.}
%   \label{tab:phaseb-b2}
%   \footnotesize
%   \resizebox{\textwidth}{!}{\footnotesize\begin{tabular}{lp{5.5cm}ccccccccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N Acc.} & \textbf{F1 Yes} & \textbf{F1 No} & \textbf{Y/N M-F1} & \textbf{Fact. S.} & \textbf{Fact. L.} & \textbf{F. MRR} & \textbf{List P.} & \textbf{List F1} \\
%     \midrule
%     bioinfo-0 & Agents v1 (3-open-27-120b) & 0.8571 (27) & 0.8800 (30) & 0.8235 (20) & 0.8518 (23) & 0.2500 (24) & 0.2500 (38) & 0.2500 (35) & 0.4369 (21) & 0.3836 (26) \\
%     bioinfo-1 & Agents v2 (5-mixed) & 0.9048 (6) & 0.9286 (11) & 0.8571 (9) & 0.8929 (9) & 0.3000 (16) & 0.3500 (19) & 0.3250 (18) & 0.2266 (57) & 0.2270 (57) \\
%     bioinfo-2 & Agents v4 [S] (3-gemma-27-31b) & 0.9048 (6) & 0.9286 (11) & 0.8571 (9) & 0.8929 (9) & 0.3000 (16) & 0.3000 (29) & 0.3000 (23) & 0.3657 (38) & 0.3709 (35) \\
%     bioinfo-3 & LLM-as-judge + ensemble summarization (mixed) & 0.9048 (6) & 0.9286 (11) & 0.8571 (9) & 0.8929 (9) & 0.3000 (16) & 0.3000 (29) & 0.3000 (23) & 0.4137 (28) & 0.4366 (18) \\
%     bioinfo-4 & Ensemble (Gemini + Nemotron + Pixa) exact + Sonnet 4.6 ideal & 0.8571 (27) & 0.8800 (30) & 0.8235 (20) & 0.8518 (23) & 0.3500 (11) & 0.3500 (19) & 0.3500 (12) & 0.4308 (23) & 0.4062 (22) \\
%     \bottomrule
%   \end{tabular}
% }%
%   \par\medskip
%   \caption{Phase B ideal answer scores and rankings for Test Batch~2. Rankings shown in parentheses.}
%   \label{tab:phaseb-b2-ideal}
%   \footnotesize\begin{tabular}{llcccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
%     \midrule
%     bioinfo-3 & LLM-as-judge + ensemble summarization & 0.3386 (3) & 0.1334 (25) & 0.3550 (2) & 0.1403 (24) \\
%     bioinfo-4 & Ensemble exact + Sonnet 4.6 ideal & 0.3024 (9) & 0.1595 (17) & 0.3022 (8) & 0.1566 (16) \\
%     bioinfo-2 & Agents v4 [S] & 0.3005 (12) & 0.1903 (8) & 0.2899 (13) & 0.1807 (8) \\
%     bioinfo-1 & Agents v2 & 0.2852 (20) & 0.1527 (22) & 0.2848 (17) & 0.1522 (25) \\
%     bioinfo-0 & Agents v1 & 0.2359 (34) & 0.1766 (10) & 0.2328 (34) & 0.1704 (12) \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 3 PHASE B
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase B exact answer scores and rankings for Test Batch~3. Rankings shown in parentheses. \textbf{[S]} = small/lightweight local models, \textbf{[M]} = medium models.}
%   \label{tab:phaseb-b3}
%   \footnotesize
%   \resizebox{\textwidth}{!}{\footnotesize\begin{tabular}{lp{5.5cm}ccccccccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N Acc.} & \textbf{F1 Yes} & \textbf{F1 No} & \textbf{Y/N M-F1} & \textbf{Fact. S.} & \textbf{Fact. L.} & \textbf{F. MRR} & \textbf{List P.} & \textbf{List F1} \\
%     \midrule
%     bioinfo-0 & Agents v0 [S] (3-open-2-4b) & 0.9091 (5) & 0.9333 (16) & 0.8571 (11) & 0.8952 (12) & 0.3529 (25) & 0.4118 (29) & 0.3824 (27) & 0.4125 (18) & 0.4102 (20) \\
%     bioinfo-1 & Agents v1 [M] (4-open-26-35b) & 0.9091 (5) & 0.9333 (16) & 0.8571 (11) & 0.8952 (12) & 0.4706 (9) & 0.4706 (21) & 0.4706 (14) & 0.3706 (25) & 0.3575 (26) \\
%     bioinfo-2 & Agents v2 (5-mixed) & 0.9091 (5) & 0.9333 (16) & 0.8571 (11) & 0.8952 (12) & 0.3529 (25) & 0.4118 (29) & 0.3725 (29) & 0.3822 (21) & 0.3963 (23) \\
%     bioinfo-3 & Agents v3 (4-open-24-123b) & 0.8182 (38) & 0.8571 (40) & 0.7500 (32) & 0.8036 (35) & 0.3529 (25) & 0.4118 (29) & 0.3824 (27) & 0.3840 (19) & 0.4053 (17) \\
%     bioinfo-4 & Agents v4 (3-mistral-129-695b) & 0.9091 (5) & 0.9333 (16) & 0.8571 (11) & 0.8952 (12) & 0.4706 (9) & 0.5294 (10) & 0.5000 (10) & 0.3866 (20) & 0.3763 (25) \\
%     \bottomrule
%   \end{tabular}
% }%
%   \par\medskip
%   \caption{Phase B ideal answer scores and rankings for Test Batch~3. Rankings shown in parentheses.}
%   \label{tab:phaseb-b3-ideal}
%   \footnotesize\begin{tabular}{llcccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
%     \midrule
%     bioinfo-3 & Agents v3 & 0.2734 (8) & 0.1732 (26) & 0.2704 (8) & 0.1716 (26) \\
%     bioinfo-1 & Agents v1 [M] & 0.2495 (15) & 0.1700 (29) & 0.2464 (18) & 0.1651 (28) \\
%     bioinfo-4 & Agents v4 & 0.2487 (16) & 0.1661 (32) & 0.2570 (13) & 0.1678 (27) \\
%     bioinfo-0 & Agents v0 [S] & 0.2472 (17) & 0.1815 (18) & 0.2438 (16) & 0.1774 (18) \\
%     bioinfo-2 & Agents v2 & 0.2368 (20) & 0.1680 (31) & 0.2402 (20) & 0.1701 (24) \\
%     \bottomrule
%   \end{tabular}
% \end{table}

% % ============================================================
% % BATCH 4 PHASE B
% % ============================================================
% \begin{table}[ht]
%   \centering
%   \caption{Phase B exact answer scores and rankings for Test Batch~4. Rankings shown in parentheses. \textbf{[S]} = small/lightweight local models.}
%   \label{tab:phaseb-b4}
%   \footnotesize
%   \resizebox{\textwidth}{!}{\footnotesize\begin{tabular}{lp{5.5cm}ccccccccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{Y/N Acc.} & \textbf{F1 Yes} & \textbf{F1 No} & \textbf{Y/N M-F1} & \textbf{Fact. S.} & \textbf{Fact. L.} & \textbf{F. MRR} & \textbf{List P.} & \textbf{List F1} \\
%     \midrule
%     bioinfo-0 & Agents v0 [S] (3-open-2-4b) & 0.9375 (5) & 0.9474 (8) & 0.9231 (7) & 0.9352 (7) & 0.2727 (18) & 0.3636 (19) & 0.3182 (19) & 0.3695 (40) & 0.3809 (41) \\
%     bioinfo-1 & Agents v1 (2-gemma-4-26-31b) & 0.8750 (31) & 0.9000 (31) & 0.8333 (26) & 0.8667 (28) & 0.1818 (29) & 0.2727 (36) & 0.2273 (35) & 0.4867 (24) & 0.4858 (22) \\
%     bioinfo-2 & Agents v2 (4-mixed-b4) & 0.8750 (31) & 0.9000 (31) & 0.8333 (26) & 0.8667 (28) & 0.3636 (10) & 0.4545 (9) & 0.4091 (9) & 0.4442 (29) & 0.4763 (25) \\
%     bioinfo-3 & Agents v3 (3-qwen-mixed-27-35b) & 0.8750 (31) & 0.9000 (31) & 0.8333 (26) & 0.8667 (28) & 0.4545 (4) & 0.5455 (4) & 0.5000 (5) & 0.5583 (15) & 0.5671 (11) \\
%     bioinfo-4 & Agents v5 (2-mistral-129-695b) & 0.9375 (5) & 0.9474 (8) & 0.9231 (7) & 0.9352 (7) & 0.3636 (10) & 0.4545 (9) & 0.3939 (11) & 0.3816 (37) & 0.3862 (39) \\
%     \bottomrule
%   \end{tabular}
% }%
%   \par\medskip
%   \caption{Phase B ideal answer scores and rankings for Test Batch~4. Rankings shown in parentheses.}
%   \label{tab:phaseb-b4-ideal}
%   \footnotesize\begin{tabular}{llcccc}
%     \toprule
%     \textbf{System} & \textbf{Generation Configuration} & \textbf{R-2 Rec.} & \textbf{R-2 F1} & \textbf{R-SU4 Rec.} & \textbf{R-SU4 F1} \\
%     \midrule
%     bioinfo-1 & Agents v1 & 0.2716 (8) & 0.1566 (28) & 0.2678 (8) & 0.1543 (29) \\
%     bioinfo-2 & Agents v2 & 0.2682 (11) & 0.1714 (22) & 0.2698 (6) & 0.1698 (19) \\
%     bioinfo-4 & Agents v5 & 0.2496 (18) & 0.1526 (31) & 0.2477 (18) & 0.1496 (31) \\
%     bioinfo-0 & Agents v0 [S] & 0.2472 (19) & 0.1742 (15) & 0.2480 (17) & 0.1729 (15) \\
%     bioinfo-3 & Agents v3 & 0.2401 (21) & 0.1452 (33) & 0.2484 (14) & 0.1467 (32) \\
%     \bottomrule
%   \end{tabular}
% \end{table}

\paragraph{Phase B Analysis.}
Phase~B results, using gold-standard documents, isolate the generation capability of each system from retrieval quality. Several consistent patterns emerged.

\textbf{Small model agents remain competitive.} Agents v0 [S] (Gemma-4-E4B/E2B + Nemotron-3-Nano-4B) achieved strong results across batches. In Batch~3, Agents v0 [S] matched the Y/N accuracy of all other systems (0.9091, rank~5) and achieved the best ideal answer F1 scores in the batch (R-2 F1: 0.1815, rank~18; R-SU4 F1: 0.1774, rank~18). In Batch~4, Agents v0 [S] achieved the highest Y/N accuracy (0.9375, rank~5) alongside Agents v5, and the best R-2 F1 (0.1742, rank~15) among our submissions. These results confirm that lightweight local models, when provided with gold-standard evidence, can generate answers whose quality rivals or exceeds much larger models. The key advantage appears to be in precision-oriented metrics (F1 scores), where smaller models produce more focused, less verbose answers.

\textbf{Agent model family specialization.} Different agent configurations showed distinct strengths. Agents v3 (Qwen3.6 family in Batch~4) excelled at factoid and list questions, achieving 4th in factoid strict accuracy (0.4545) and 11th in list F-Measure (0.5671)---our strongest factoid result across all batches. Agents v4 (Mistral family in Batch~3) achieved the best factoid lenient accuracy (0.5294, rank~10) and factoid MRR (0.5000, rank~10). Agents v2 (large proprietary models) performed best on Y/N questions but showed weaker list and factoid precision. The Mistral-family agents (v4, v5) consistently produced strong factoid results across batches, suggesting that the Mistral model family may have particular strengths in biomedical fact extraction.

\textbf{LLM-as-judge.} The LLM-as-judge approach was used in Batch~1 Phase~B (both submissions) and Batch~2 Phase~A+ (\texttt{bioinfo-3}, \texttt{bioinfo-4}). In Phase~B Batch~1, LLM-as-judge top-k=5 (\texttt{bioinfo-1}) outperformed top-k=3 (\texttt{bioinfo-0}) on factoid metrics (strict accuracy 0.4348 vs.\ 0.3913; MRR 0.4565 vs.\ 0.4130) but underperformed on ideal answers (R-2 F1 0.0958 vs.\ 0.1303), suggesting a recall-precision trade-off with increasing k. In Phase~A+ Batch~2, LLM-as-judge systems achieved top-10 list recall (ranks 5--7) but weaker Y/N and factoid performance compared to agent-based systems, consistent with a method optimized for coverage over precision.

\textbf{Ideal answer recall vs.\ precision.} Across all batches, ideal answer recall ranks were notably stronger than F1 ranks---\texttt{bioinfo-3} achieved 3rd in R-2 and R-SU4 recall in Batch~2, and several systems achieved top-10 recall ranks in Batches~3--4. This pattern, consistent with our findings from the 13th edition, suggests that our systems tend to produce comprehensive answers that cover relevant content but may include extraneous information that reduces precision-oriented metrics. The small model agents (v0 [S]) partially mitigated this trade-off, achieving the best F1 scores while maintaining competitive recall, likely due to their more constrained output length.
