%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout. Do not use twocolumn for papers submitted to CEUR-WS!
%% hf: enable header and footer.
\documentclass[
  % twocolumn,
  % hf,
]{ceurart}

\usepackage{tabularx}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{booktabs}
%%
%% One can fix some overfulls
\sloppy

%%
%% Minted listings support
%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
\usepackage{listings}
\usepackage{todonotes}
\usepackage{graphicx}

\usetikzlibrary{backgrounds, fit, positioning, arrows.meta}
%% auto break lines
\lstset{breaklines=true}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2026}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{CLEF 2026 Working Notes, 21 -- 24 September 2026, Jena, Germany}

%%
%% The "title" command
\title{BIT.UA at BioASQ 14B: Modular Retrieval with pg\_textsearch and Qdrant, and Agent-Based Answer Generation}

\title[mode=sub]{BIT.UA at CLEF 2026}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[2]{André Ribeiro}[%
  orcid=0009-0008-0194-7171,
  email=andrepedroribeiro@ua.pt,
]
\cormark[1]

\author[1]{Rúben Garrido}[%
  orcid=0009-0002-1508-7885,
  email=rubengarrido@ua.pt,
]
\cormark[1]

\author[3]{Alexander Christiansen}[%
  orcid=0009-0003-3867-7324,
  email=ach22@student.aau.dk,
]

\author[1,3]{Richard A. A. Jonker}[%
  orcid=0000-0002-3806-6940,
  email=richard.jonker@ua.pt,
]

% \author[1]{Tiago Almeida}[%
%   orcid=0000-0002-4258-3350,
%   email=tiagomeloalmeida@ua.pt,
% ]

\author[1]{Sérgio Matos}[%
  orcid=0000-0003-1941-3983,
  email=aleixomatos@ua.pt,
]

% \author[1]{João R. Almeida}[%
%   orcid=0000-0003-0729-2264,
%   email=joao.rafael.almeida@ua.pt,
% ]
\address[1]{IEETA/DETI, LASI, University of Aveiro, Aveiro, Portugal}
\address[2]{IT, University of Aveiro, Aveiro, Portugal}
\address[3]{Aalborg University Business School, Aalborg, Denmark}

%% Footnotes
\cortext[1]{Corresponding author.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  This paper describes the participation of the BIT.UA team from the University of Aveiro in the 14th edition of the BioASQ Task B challenge on biomedical question answering. Building on our previous submissions, we introduced a substantially refactored and modular codebase, and made significant changes to both the retrieval and generation components of the pipeline. For Phase~A document retrieval, we replaced the PyTerrier PISA index with PostgreSQL-based pg\_textsearch for BM25 retrieval and adopted Qdrant for dense embedding indexing, enabling more efficient storage and GPU-accelerated similarity search. We explored HyDE-based query expansion alongside a Context-1 retrieval strategy. A new reranker training pipeline was developed, incorporating dense retrieval for negative sampling. For Phases A+ and B answer generation, we introduced an LLM-as-a-judge framework and a novel agent quorum mechanism, where multiple agents with diverse prompts debate and iteratively converge on a consensus answer using adaptive document retention. We also participated in the snippets generation subtask for the first time. Our systems achieved competitive results across all batches, with Phase~A systems achieving MAP ranks of 6 (Batch~1), 7 (Batch~3), and top-10 in Batches~1,~3,~and~4. We discuss the impact of these architectural changes, lessons learned, and outline directions for future work including SPLADE and ColBERT integration. All code is openly available: \url{https://github.com/bioinformatics-ua/BioASQ14b}.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  Information Retrieval \sep
  Document Retrieval \sep
  Dense Retrieval \sep
  Large Language Model \sep
  Answer Generation \sep
  Multi-Agent Systems \sep
  Biomedical Question Answering
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
% \todo[inline]{github+acknowledgements}
\input{chapters/introduction}
\input{chapters/previous-work}
\input{chapters/methodology/common}
\input{chapters/results/common}
\input{chapters/discussion}
\input{chapters/conclusion}

\begin{acknowledgments}
  This work was funded by FEDER - Fundo Europeu de Desenvolvimento Regional funds through Programa Regional do Centro, within project CENTRO2030-FEDER-02595400 and by the Foundation for Science and Technology (FCT) through the contract \url{https://doi.org/10.54499/UID/00127/2025}. Richard A. A. Jonker is funded by the FCT doctoral grant PRT/BD/154792/2023,
  with DOI identifier \url{https://doi.org/10.54499/PRT/BD/154792/2023}.
\end{acknowledgments}

%% https://ceur-ws.org/GenAI/Policy.html
\section*{Declaration on Generative AI}
% {\em Either:}\newline
% The author(s) have not employed any Generative AI tools.
% \newline

During the preparation of this work, the authors used various generative models in order to correct grammar, spelling check, and paraphrase text within this document. After using these tool(s)/service(s), the author(s) reviewed and edited the content as needed and take(s) full responsibility for the publication’s content.

% \noindent{\em Or (by using the activity taxonomy in ceur-ws.org/genai-tax.html):\newline}
% During the preparation of this work, the author(s) used X-GPT-4 and Gramby in order to: Grammar and spelling check. Further, the author(s) used X-AI-IMG for figures 3 and 4 in order to: Generate images. After using these tool(s)/service(s), the author(s) reviewed and edited the content as needed and take(s) full responsibility for the publication’s content.

\bibliography{references}

\input{chapters/appendix}

\end{document}
