% The generation phase underwent its most substantial revision in this edition, with two major innovations: an LLM-as-a-judge framework and a multi-agent quorum mechanism.

\subsection{Answer Generation}

Once relevant documents and snippets have been retrieved, the system must produce a final answer to the biomedical question. Rather than relying on a single generation call, this edition explores two complementary strategies for combining and refining candidate outputs from multiple models: an LLM-as-a-judge framework that evaluates and selects among independently generated answers, and an agent quorum mechanism that has multiple models debate and converge on a shared answer. Both approaches aim to improve robustness over simple majority voting by incorporating richer signals about correctness, evidentiary support, and completeness. The following subsections describe each in detail.

\subsubsection{Majority Voting}

For Batch 1, we employed previous editions' majority voting as the primary method for aggregating outputs from multiple generation models. Each model produces an answer independently given the same question and context, and the final answer is selected by a fixed, rule-based aggregation strategy that varies by question type. For yes/no questions, a simple majority vote is taken: whichever answer (``yes'' or ``no'') appears most frequently across model outputs wins, with ties defaulting to ``yes.'' For factoid questions, which ask for a specific named entity, models produce ranked lists of up to five candidates. These lists are merged via Reciprocal Rank Fusion (RRF): each candidate receives a score equal to the sum of $1 / (rank + k)$ across all input lists, with $k = 60$, and the top five candidates by fused score are returned. For list questions, entities that appear in at least a threshold fraction of the input sets (defaulting to a strict majority, i.e., 50\% of models) are retained in the final output. This approach is straightforward and computationally inexpensive, but it treats all models as equally reliable and provides no mechanism for evaluating whether a candidate answer is actually supported by the retrieved evidence.

\subsubsection{LLM as a Judge}
\label{sec:llm-judge}

For this edition, we replaced majority voting with an LLM-as-a-judge framework. Rather than applying a fixed aggregation rule, a separate LLM instance evaluates the outputs of different generation models and either selects the best candidate answer or synthesizes a superior answer by combining elements from multiple outputs. The judge model receives all candidate answers along with the original question, the question type, the retrieved context, and (when available) reference ideal answers. It is prompted to score each candidate answer along multiple dimensions (correctness, faithfulness to the provided context, and completeness) on a 0--1 scale, with an accompanying rationale.

The judge's system prompt establishes it as a biomedical question-answering evaluator that outputs a structured JSON object containing numerical scores and a concise rationale. As stated before, the scoring dimensions are: \emph{correctness} (factual accuracy of the answer), \emph{faithfulness} (whether claims are grounded in the retrieved context), \emph{completeness} (whether all aspects of the question are addressed), and \emph{overall} (a holistic quality judgment). This multi-dimensional evaluation provides a richer signal than binary voting and allows the pipeline to prefer answers that are well-supported by evidence, even if they are not the most similar to the majority opinion.

The motivation for adopting an LLM judge over majority voting is twofold. First, an LLM can critically evaluate the evidence grounding of each answer, penalizing hallucinations that a voting scheme would not detect. Second, the judge can identify complementary information across different candidate answers and either select the most comprehensive one or, in some configurations, synthesize a hybrid answer. This flexibility is particularly valuable for ideal answer generation, where different models may emphasize different aspects of the evidence.

In practice, the LLM judge proved especially effective for exact answer types (yes/no, factoid, list), where correctness is more objectively verifiable against context.

\subsubsection{Agent Quorum Mechanism}

The most significant methodological innovation for this edition is the agent quorum, a multi-agent debate framework designed to produce more robust and well-reasoned answers. The mechanism operates as follows.

\textbf{Agent configuration and thinking focuses.} Multiple agents are instantiated, each with a potentially different LLM and a distinct cognitive focus that shapes how they approach the evidence. The available focuses, drawn from a predefined pool, include: \emph{analytical} (systematically decomposing evidence and identifying logical chains), \emph{evidence-based} (grounding every claim strictly in the provided documents and flagging contradictions between sources), \emph{skeptical} (challenging the debate's direction, seeking gaps in evidence, alternative interpretations, and methodological limitations), \emph{integrative} (synthesizing information across all sources and reconciling apparent contradictions), \emph{pragmatic} (focusing on the most direct, actionable answer and prioritizing precision), and \emph{theoretical} (considering underlying biological mechanisms and established scientific principles). Each agent receives a system prompt that establishes it as a rigorous biomedical scientist participating in a structured expert debate, responding exclusively with valid JSON.

\textbf{Adaptive document retention.} Documents and their corresponding snippets are provided to agents through an adaptive retention protocol. Initially, each agent receives three randomly selected documents from the retrieval set. After analyzing these documents, each agent decides which documents to retain. If an agent retains fewer than three documents, its next round includes those retained documents plus additional randomly selected documents to bring the total back to three. If an agent retains all three, the next round includes four documents (the three retained plus one new random document), and so on. This mechanism allows agents to maintain focus on the documents they deem most relevant while preserving some diversity in the evidence pool, preventing premature convergence on suboptimal information.

\textbf{Debate and scoring.} In each round, every agent produces both an opinion (its current best answer to the question with detailed reasoning) and an agreement level drawn from the set $\{\text{strongly\_disagree}, \text{disagree}, \text{agree}, \text{strongly\_agree}\}$. Agents are ordered randomly in each round to prevent anchoring effects. During the debate, agents are shown the opinions and agreement levels of all other agents from the current round and are instructed to engage critically: if another agent cites evidence they have not seen, they weigh those claims against their own documents; if they disagree, they explain what specific evidence or reasoning undermines the opposing position; if they agree, they strengthen the argument with additional evidence from their documents. Agents are explicitly warned against premature agreement and are instructed to output \texttt{strongly\_agree} only when genuinely confident that the answer is correct, complete, and well-supported by evidence.

\textbf{Convergence criteria.} The quorum continues for multiple rounds until one of three stopping conditions is met: (1)~all agents reach the \texttt{strongly\_agree} level, indicating full consensus; (2)~a predefined maximum number of rounds is reached; or (3)~the agreement levels remain unchanged for a specified number of consecutive rounds (default: 3), indicating a stable disagreement that further debate is unlikely to resolve.

\textbf{Final summarization.} Once the quorum concludes, a designated synthesizer model consolidates all debate turns into a single final answer. This model receives the original question, the full set of context documents, and a structured summary of the debate. It is instructed to produce a definitive answer based solely on the evidence in the context documents, informed by the reasoning developed during the debate, without referencing the debate process itself.

\textbf{Agent configurations across batches.} The models and thinking focuses used in the agent quorum evolved across batches as we experimented with different configurations. Table~\ref{tab:quorum-batches} summarizes the agent configurations used in each test batch.

\begin{table}[ht]
  \centering
  \caption{Agent quorum configurations across test batches. Agents are listed with their model identifier and the synthesizer used for final answer generation. The \textbf{Config} code encodes the number of agents, weight openness (\texttt{open} = all weights public, \texttt{mixed} = some API-only), and the parameter range (in billions) across open-weight agents; \texttt{api} denotes configurations dominated by hosted closed models.}
  \label{tab:quorum-batches}
  \begin{tabularx}{\textwidth}{llX}
    \toprule
    \textbf{Batch} & \textbf{Version / Config} & \textbf{Agents (Model)} \\
    \midrule
    \multirow{8}{*}{B2}& V1 (\texttt{3-open-27-120b})      & Qwen3-Next-80B, Nemotron-3-Super-120B, MedGemma-27B \\
    &                                      & Synthesizer: Nemotron-3-Super-120B \\
    & V2 (\texttt{5-mixed})                & Nemotron-3-Super-120B, Grok-4.1-Fast, Gemini-3-Flash, Gemini-2.5-Flash, GPT-5-Mini \\
    &                                      & Synthesizer: Claude-Sonnet-4.6 \\
    & V3 (\texttt{4-open-35-309b})         & Qwen3-Next-80B, Mimo-v2-Flash (309B), Qwen3.5-35B, Nemotron-3-Super-120B \\
    &                                      & Synthesizer: GPT-5.4-Nano \\
    & V4 (\texttt{3-open-26-31b})          & Gemma-4-31B, Gemma-4-26B, MedGemma-27B \\
    &                                      & Synthesizer: Gemma-4-31B \\
    \midrule
    \multirow{8}{*}{B3} & V0 (\texttt{3-open-2-4b})         & Gemma-4-E4B, Gemma-4-E2B, Nemotron-3-Nano-4B \\
    &                                      & Synthesizer: Gemma-4-E4B \\
    & V1 (\texttt{4-open-26-35b})          & Gemma-4-26B, Gemma-4-31B, Nemotron-3-Nano-30B, Qwen3.5-35B \\
    &                                      & Synthesizer: Gemma-4-26B \\
    & V2 (\texttt{5-mixed-api})            & Nemotron-3-Super-120B, Grok-4.1-Fast, Gemini-3-Flash, Gemini-2.5-Flash, GPT-5-Mini \\
    &                                      & Synthesizer: Gemini-2.5-Flash \\
    & V3 (\texttt{4-open-24-675b})         & Gemma-4-31B, Qwen3.5-35B, Mistral-Small-4 (119B), Mistral-Large-3 (675B) \\
    &                                      & Synthesizer: Mistral-Small-4 (119B) \\
    \midrule
    \multirow{10}{*}{B4} & V0 (\texttt{3-open-2-4b})         & Gemma-4-E4B, Gemma-4-E2B, Nemotron-3-Nano-4B \\
    &                                      & Synthesizer: Gemma-4-E4B \\
    & V1 (\texttt{2-gemma-4-26-31b})       & Gemma-4-26B, Gemma-4-31B \\
    &                                      & Synthesizer: Gemma-4-26B \\
    & V2 (\texttt{4-mixed-api})            & Nemotron-3-Super-120B, Gemini-3-Flash, Gemini-2.5-Flash, GPT-5-Mini \\
    &                                      & Synthesizer: Gemini-2.5-Flash \\
    & V3 (\texttt{3-qwen-27-35b})    & Qwen3.6-35B, Qwen3.6-27B, Qwen3.6-Flash \\
    &                                      & Synthesizer: Qwen3.6-35B \\
    & V4 (\texttt{3-mistral-129-695b})     & Mistral-Medium-3.5 (128B), Mistral-Small-4 (119B), Mistral-Large (695B) \\
    &                                      & Synthesizer: Mistral-Medium-3.5 (128B) \\
    & V5 (\texttt{2-mistral-120B})         & Mistral-Medium-3.5 (128B), Mistral-Small-4(119B) \\
    &                                      & Synthesizer: Mistral-Medium-3.5 (128B)\\
    \bottomrule
  \end{tabularx}
\end{table}