\subsection{First-Stage Retrieval}
\label{sec:first-stage}

The first stage of our retrieval pipeline performs parallel lexical and dense search over the PubMed corpus, then fuses the results into a single candidate list for subsequent re-ranking. In previous years we relied solely on BM25 as a first stage retrieval model, however this year we experimented with hybrid retrieval combining both dense retrieval with BM25.

\subsubsection{BM25 Retrieval via pg\_textsearch}

In previous editions, we relied on the PISA indexing framework~\cite{mallia2019pisa} accessed through the PyTerrier interface for BM25-based first-stage retrieval. While effective, this approach required loading indexes from disk (slow by design) to memory at each pipeline iteration and maintaining them as separate artifacts from document storage.

For the 14th edition, we migrated BM25 retrieval to PostgreSQL using the pg\_textsearch extension~\cite{pgtextsearch}, an external module that provides full-text search capabilities. This change integrated document storage and full-text search into a single source of truth, eliminating the need for separate index files. The PostgreSQL GiN (Generalized Inverted Index) indexes are maintained automatically alongside document updates, and the entire pipeline now operates on a single database. The BM25 index was configured with parameters $k_1 = 0.4$ and $b = 0.3$, values determined empirically on held-out data. The key improvement is in usability and maintainability: document ingestion, index updates, and retrieval queries all happen within the same system, reducing operational complexity and the risk of synchronization errors between document versions and retrieval indexes.

\subsubsection{Dense Retrieval with Qdrant and BGE-M3}

This year we introduced dense retrieval as a first-stage retrieval method, moving beyond our previous use of dense embeddings solely for Pseudo Relevance Feedback. For embedding generation, we deployed the BGE-M3 model~\cite{chen2024bge} (569M parameters) via the Text Embeddings Interface (TEI) from Hugging Face. BGE-M3 is a multi-lingual, multi-functional embedding model that produces dense vectors suitable for semantic similarity search in the biomedical domain.

TEI is a Rust-based implementation optimized for serving text embeddings. A key architectural advantage of TEI is its API-based design, which decouples embedding generation from the main pipeline process. This allows deploying multiple TEI instances in parallel, scaling horizontally to meet the throughput demands of indexing the full PubMed corpus. TEI provides tokenization and model inference in a single binary supporting both CPU and GPU execution.

The generated embeddings are indexed and stored in Qdrant, a vector database that supports GPU-accelerated approximate nearest neighbor search via HNSW (Hierarchical Navigable Small World) indexing. This replaces our previous approach of precomputing and storing all cross-embedding similarities as flat NumPy arrays---a practice that became increasingly untenable as the document corpus grew. Qdrant provides compact storage, configurable precision-speed tradeoffs, and dynamic collection management with metadata filtering, enabling efficient incremental updates as new documents are indexed.

At query time, the question text (or its HyDE expansion, described below) is encoded via the same TEI endpoint and searched against the Qdrant index. The top 100 dense-retrieved documents are then combined with the top 100 BM25-retrieved documents through fusion.

\subsubsection{Hybrid Fusion}

To combine the BM25 and dense retrieval results into a single candidate list, we evaluated two approaches, weighted sum and Reciprocal Rank Fusion (RRF). The weighted sum method combines scores linearly:

\begin{equation}
  S_{ws}(d) = \alpha \cdot S_{bm25}(d) + (1 - \alpha) \cdot S_{dense}(d)
\end{equation}

where $S_{bm25}(d)$ and $S_{dense}(d)$ are normalized scores from each retrieval method and $\alpha \in [0,1]$ controls the relative contribution of each. We used $\alpha = 0.6$, giving slightly more weight to BM25, which was found to perform well on validation data. While straightforward, this method is sensitive to the scale and distribution of the individual scores, since BM25 and dense similarity scores have different ranges and statistical properties.

Reciprocal Rank Fusion (RRF) provides an alternative that operates on ranks rather than raw scores, making it robust to heterogeneous score distributions. We discuss RRF in the context of re-ranking fusion in Section~\ref{sec:fusion}, as it is primarily used to fuse the outputs of multiple rerankers. For first-stage fusion, both weighted sum and RRF were evaluated; their comparative performance is reported in Section~\ref{sec:results}.

\subsubsection{Query exapnsion: HyDE}
\label{sec:query-expansion}

Query expansion improves information retrieval by augmenting the initial search with related terms or context to capture a broader intent. Hypothetical Document Embeddings (HyDE) replaces the original query with a hypothetical answer generated by an LLM. Rather than embedding the user's question directly, the LLM is prompted to produce a plausible answer, and this generated text is embedded via TEI and used as the query for dense retrieval. The intuition is that an LLM-generated answer, even if factually incomplete or partially incorrect, shares the linguistic and conceptual structure of genuinely relevant documents more closely than the original question does. When HyDE is enabled, the dense retrieval branch of the first-stage pipeline uses the HyDE embedding instead of the raw question embedding; the BM25 branch continues to use the original query text.

\subsubsection{Agent retrieval: Context-1}

Context-1~\cite{context1} is a 20B-parameter model purpose-trained for multi-turn, agentic search over document collections. Unlike single-pass retrieval pipelines or query expansion methods, Context-1 operates as a retrieval subagent that iteratively decomposes a high-level question into sub-queries, retrieves documents, evaluates their relevance, and refines its search strategy across multiple turns.

The model actively manages its own context window. As it accumulates documents over successive retrieval turns, it selectively discards irrelevant passages through a pruning mechanism, freeing context capacity for further exploration. This self-editing behavior addresses a key limitation of multi-turn retrieval: the tendency of the context window to fill with tangential material. The agent interacts with the underlying search infrastructure through structured tool calls---searching the corpus, reading full documents, and pruning irrelevant chunks---within a fixed token budget that forces explicit relevance judgments.

In our pipeline, Context-1 serves as a retrieval subagent that receives the original BioASQ question and iteratively searches our indexed PubMed collection (via BM25 and dense search tools), internally using the BGE-reranker-v2-m3 cross-encoder to score retrieved candidates. The output of Context-1 is a ranked set of documents, which we then feed through our own ensemble of rerankers for the final ranking. Since Context-1 is a recent project, only the model was available at the time, where we implemented a harness based on the description in the original paper. We implemented the necessary tool interfaces for BM25 and dense search, as well as the pruning mechanism to manage the context window.

\subsection{Re-Ranking}
\label{sec:reranking}

% \subsubsection{Reranker Training Pipeline}

We developed a new, flexible training pipeline for cross-encoder rerankers. The pipeline supports multiple base models, training strategies, and data configurations. A notable improvement was the incorporation of dense retrieval for negative sampling. In previous editions, negative examples for reranker training were selected exclusively from BM25 results, which limited the diversity of negatives. By including dense retrieval results in the negative generation process, the reranker is exposed to a broader range of challenging distractors, improving its ability to distinguish relevant from irrelevant documents across different retrieval paradigms.

We trained a total of 29 reranker models based on diverse architectures including BGE-reranker-v2-m3, PubMedBERT, BioLinkBERT, BioBERT, MedCPT, and the LLaMA Nemotron reranker, among others. Training employed a pairwise loss with varying configurations of epochs, samplers, and hard negative counts. A complete listing of the trained models and their configurations is provided in Appendix~\ref{sec:appendix-models}.

\subsubsection{Reciprocal Rank Fusion (RRF)}
\label{sec:fusion}

To combine the outputs of multiple rerankers into a single ranked list, we employ Reciprocal Rank Fusion (RRF). RRF combines rankings based solely on reciprocal positions rather than raw scores, making it robust to score scale differences between heterogeneous models. The RRF score for a document $d$ is computed as:

\begin{equation}
  RRF(d) = \sum_{r \in R} \frac{1}{k + rank_r(d)}
\end{equation}

where $R$ is the set of reranker runs and $k$ is a constant (typically 60) that mitigates the impact of high-ranked documents dominating the final score. Because RRF operates on ranks rather than scores, it requires no normalization and is insensitive to the magnitude of individual reranker scores. This is particularly important when combining rerankers of different architectures (e.g., BERT-based and decoder-based models) whose score distributions differ substantially. In our experiments, RRF consistently outperformed weighted sum for reranker fusion, as the rank-based approach naturally handles heterogeneous score scales without requiring per-batch calibration.

\subsection{Snippet Generation via Fine-Tuned Gemma 4}

For the first time, we participated in the snippet generation subtask. Given a question and a set of retrieved documents, the system must identify the most relevant text spans within those documents. We approached this as a text generation problem: a model receives the question along with a document's title and abstract, and generates the most relevant snippets from that document.

We fine-tuned a Gemma~4~31B model using QLoRA (Quantized Low-Rank Adaptation) for this task. The training data was derived from the snippet annotations provided in the BioASQ training set, where for each question-document pair, the gold-standard snippets were extracted from the document text. The model was trained in a chat format, receiving the question and document content as input and producing the corresponding snippets as output. The LoRA adapters were applied to the attention projection layers, enabling efficient fine-tuning with substantially reduced memory requirements compared to full fine-tuning.
